---
title: "Chapter 3: Physiology"
author: "CBB"
runtime: shiny
output: 
  html_document:
    theme: spacelab
---
# Results

#### (A) Individual coral host and algal endosymbiont physiology
> Protein: .  
Lipids: .  
Carbs: .  
Density: .  
Chla: .  


#### (B) Total coral host energy reserves
> Coral host total energy reserves (mg/cm2) was calculated as the sum of each protein, lipid, and carbohydrate value per fragment. 

(**Figure 2A**). 

#### (C) Total algal endosymbiont physiology
> Calculated chlorophyll a content per algal endosymbiont cell (ug/10^6 cells) represents total algal endosymbiont physiology and is a measure of the efficiency of the endosymbionts within each coral fragment. Total endosymbiont physiology of *S. siderea* and *P. astreoides* did not change from the start (T0) to finish (T90) of the experimental period, nor did *p*CO2 or temperature have a statistically clear impact after 93 days at treatment. Conversely, *P. strigosa* total endosymbiont physiology increased in the 400 uatm 28C treatment at T90 compared to T0, however, there was no statistically clear difference from the other 28C *p*CO2 treatments at T90. Additionally, T90 total endosymbiont physiology was clearly greater at 31C than measured values at T0 and under all *p*CO2 treatments at 28C, except the extreme where they converge (**Figure 2B**). 

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library("knitr")

```

```{r packages, include=FALSE}

#Packages to load
library("readr")
library("ggplot2")
library("dplyr")
library("tidyr")
library("plotly")
library("tidyverse")
library("shiny")
library("Rmisc")
library("cowplot")
library("ggfortify")
library("kableExtra")
library("readr")
library("lme4")
library("magick")

```

```{r labels, include=FALSE}

#Set some standards and units
#dodge width
dodge=position_dodge(width=0.3)
dodge2=position_dodge(width = 0.6)
jitter=position_jitter(width=0.1)

theme_set(theme_classic())

# set parameter labels
Tlab<-"Temperature (°C)"
alab<-expression(paste(italic("p"),"CO" [2]~ "("*mu,'atm)'))
dlab<-expression(paste("Cell density (10"^6,"cells cm"^-2,")"))
plab<-expression(paste("Total protein (mg cm"^-2,")"))
calab<-expression(paste("Carbohydrate (mg cm"^-2,")"))
clab<-expression(paste("Chlorophyll a ("*mu,"g cm"^-2,")"))
rlab<-expression(paste("Calcification rate (mg cm"^-2~"day"^-1,")"))
llab<-expression(paste("Total Lipid (mg cm"^-2,")"))
date <- Sys.Date() 

```

```{r add phys params, include=FALSE}

# Set up the dataframes
#phys <- read_csv("phys_all_13Aug19.csv")
#
#lipid <- read_csv("~/Dropbox/Boston_Experiment/Physiology/Lipids/Calculated Lipid #Spreadsheets/Lipid_final_21Oct19.csv")
#
#lipid <- lipid[,c(2,22)]
#
#df<-phys %>% 
# left_join(lipid, by=c("coral" = "coral"))

 #write.csv(df, file="phys_all_21Oct19.csv")

```

```{r initial dataframe, include=FALSE}

df <- read_csv("phys_all_21Oct19.csv")

df$X1 <- NULL
df$X1_1 <- NULL
names(df)[38]<-"carb"
names(df)[39]<-"lipid"
df$ftemp <- as.factor(df$ftemp)
df$fpco2 <- as.factor(df$fpco2)
df$colony <- as.factor(df$colony)
df$species <- factor(df$species, levels = c("S", "P", "A", "T"))
df$fpco2 <- factor(df$fpco2, c("280", "400", "700", "2800"))
df$den <- df$den / 1000000
df$symb <- (df$chla) / (df$den)
df$host <- df$pro + df$carb + df$lipid
df$treat[df$T0_T90 == "T0"] <- "T0"
df$treat <- factor(df$treat, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

# add a new treat column for plotting
df$treat2 <- df$treat
df$treat <- gsub("T0", 2, df$treat)
df$treat <- gsub("288_28", 4, df$treat)
df$treat <- gsub("311_31", 4.5, df$treat)
df$treat <- gsub("447_28", 6, df$treat)
df$treat <- gsub("405_31", 6.5, df$treat)
df$treat <- gsub("673_28", 8, df$treat)
df$treat <- gsub("701_31", 8.5, df$treat)
df$treat <- gsub("3285_28", 10, df$treat)
df$treat <- gsub("3309_31", 10.5, df$treat)

df$treat <- as.numeric(df$treat) #convert 'treat' column to numerics

df2 <- df[,c(1:16,38:42)] #subset dataframe for selected columns
df2 <- gather(df2, param, value, den:host) # make column of parameter and value
df2$param <- factor(df2$param, levels = c("pro", "carb", "lipid", "den", "chla", "host", "symb")) #relevel physiology parameters
df2$species <- revalue(x = df2$species, c("S" = "SSID", "P" = "PSTR", "A" = "PAST", "T" = "UTEN")) #relevel species

```



```{r T0 model setup, echo=FALSE}

T0.df <- subset(df2, T0_T90=="T0") # subset for only T0 values

# this function remove rows with any missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
T0.df <- completeFun(T0.df, "value") # run function to remove any missing values from "rate"

# create 2 dataframes to run two different modesl
T0.df.1 <- subset(T0.df, subset = param %in% c("chla", "symb")) # chlorophyll a and total symbiont only
T0.df.2 <- subset(T0.df, subset = param %in% c("pro", "lipid", "carb", "host", "den")) # all host and density here

### Performing the parametric bootstrapping of the model:
bootnum = 2000 # set number of iterations (we used 2000) between 999 and 9999
seed = 7 #seed to make results replicatable (our seed was 7)

```

```{r T0 model 1, echo=FALSE}

# mixed effects model and boostrapping
#T0.model1 <- lmer(value ~ species * param + (1 | colony), REML=TRUE, data = T0.df.1)
#out <- simulate(T0.model1, nsim=bootnum, seed=seed, re.form=NULL)
#boots <- apply(out, 2, function(x) predict(lmer(x ~ species * param + (1 | colony), REML=TRUE, data = T0.df.1), re.form=NA))
#boots <- cbind(predict(T0.model1,re.form=NA), boots)
#T0.df1.a <- (cbind(T0.df.1, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T0.df1.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#T0.df1.nam <- paste("T0_model1", date, sep="_") 
#T0.df1.nam <- paste(T0.df1.nam, ".csv", sep="") 
#write.csv(T0.df1.a, file=T0.df1.nam)  

```

```{r T0 model 2, echo=FALSE}

# mixed effects model and boostrapping
#T0.model2 <- lmer(value ~ species * param + (1 | colony), REML=TRUE, data = T0.df.2)
#out <- simulate(T0.model2, nsim=bootnum, seed=seed, re.form=NULL)
#boots <- apply(out, 2, function(x) predict(lmer(x ~ species * param + (1 | colony), REML=TRUE, data = T0.df.2), re.form=NA))
#boots <- cbind(predict(T0.model2,re.form=NA), boots)
#T0.df2.a <- (cbind(T0.df.2, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T0.df2.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#T0.df2.nam <- paste("T0_model2", date, sep="_") 
#T0.df2.nam <- paste(T0.df2.nam, ".csv", sep="") 
#write.csv(T0.df2.a, file=T0.df2.nam)  

```

```{r T0 compiled model, echo=FALSE}

# read in the dataframes from the two to create one compiled
T0.df1.a <- read.csv("T0_model1_2019-11-20.csv", head=T)
T0.df2.a <- read.csv("T0_model2_2019-11-20.csv", head=T)
T0.df.a <- rbind(T0.df1.a, T0.df2.a)

T0.df.a$species <- factor(T0.df.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))
T0.df.a$param <- factor(T0.df.a$param, levels = c("carb", "lipid", "pro",  "chla", "den","host", "symb"))

T0.model2.fig <- ggplot(T0.df.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),  panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="bottom", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  geom_point(data=T0.df, aes(x=species, y=value), colour="grey", alpha = 0.3, size = 2, position = dodge)+
  ylab("Value")+
  xlab("Physiology Parameter")+
  facet_wrap(~param, scales="free_y", ncol=4)+
  geom_linerange(aes(x=species, ymin=lowerci, ymax=upperci, colour=species), position = dodge, size = 1.2)
#theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))  

```

```{r coral images, echo=FALSE}

# make cowplot of all coral images
s <- cowplot::ggdraw() + cowplot::draw_image("SSID.png", scale = 0.9) 
p <- cowplot::ggdraw() + cowplot::draw_image("PSTR.png", scale = 0.9)
a <- cowplot::ggdraw() + cowplot::draw_image("PAST.png", scale = 0.9)
u <- cowplot::ggdraw() + cowplot::draw_image("UTEN.png", scale = 0.9)
corals <- cowplot::plot_grid(s, p, a, u, ncol = 4, scale=0.7)

```

```{r T90 df, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

#modify dataframe for T90 samples
T90.df <- df[,c(1:17,38:42)]
T90.df <- subset(T90.df, T0_T90=="T90")
T90.df <- gather(T90.df, param, value, den:host) # make column of parameter and value
T90.df$param <- factor(T90.df$param, levels = c("pro", "carb", "lipid", "den", "chla", "sum_bw5", "host", "symb"))
T90.df$fpco2 <- factor(T90.df$fpco2, c("280", "400", "700", "2800"))
T90.df$species <- revalue(x = T90.df$species, c("S" = "SSID", "P" = "PSTR", 
  "A" = "PAST", "T" = "UTEN"))

```



```{r protein model, echo=FALSE}

# subsetting
T90.df.pro <- subset(T90.df, param=="pro")
T0.df.pro <- subset(T0.df.a, param=="pro")
T90.df.pro <- completeFun(T90.df.pro, "value") # run function to remove any missing values from "rate"

# mixed effect model run using lmer()
#T90.pro.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.pro)
#out <- simulate(T90.pro.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.pro),re.form=NA))
#boots <- cbind(predict(T90.pro.model,re.form=NA), boots)
#T90.df.pro.a <- (cbind(T90.df.pro, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.pro.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#pro.df <- paste("Protein_model_T90", date, sep="_") 
#pro.df <- paste(pro.df, ".csv", sep="") 
#write.csv(T90.df.pro.a, file=pro.df)  

```

```{r protein figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

T90.df.pro.a <- read.csv("Protein_model_T90_2019-11-20.csv", head=T)
T90.df.pro.a$ftemp <- as.factor(T90.df.pro.a$ftemp)
T90.df.pro.a$fpco2 <- as.factor(T90.df.pro.a$fpco2)
T90.df.pro.a$species <- factor(T90.df.pro.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

pro.model.fig <- ggplot(T90.df.pro.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.pro, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.pro, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(plab)+
  xlab("")+
  geom_point(aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))  

```

```{r carb model, echo=FALSE}

# subsetting
T90.df.carb <- subset(T90.df, param=="carb")
T0.df.carb <- subset(T0.df.a, param=="carb")
T90.df.carb <- completeFun(T90.df.carb, "value") # run function to remove any missing values from "rate"
#
## mixed effect model run using lmer()
#T90.carb.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.carb)
#out <- simulate(T90.carb.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.carb),re.form=NA))
#boots <- cbind(predict(T90.carb.model,re.form=NA), boots)
#T90.df.carb.a <- (cbind(T90.df.carb, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.carb.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#
#carb.df <- paste("carbohydrate_model_T90", date, sep="_") 
#carb.df <- paste(carb.df, ".csv", sep="") 
#write.csv(T90.df.carb.a, file=carb.df)  

```

```{r carb figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

T90.df.carb.a <- read.csv("carbohydrate_model_T90_2019-11-20.csv", head=T)
T90.df.carb.a$ftemp <- as.factor(T90.df.carb.a$ftemp)
T90.df.carb.a$fpco2 <- as.factor(T90.df.carb.a$fpco2)
T90.df.carb.a$species <- factor(T90.df.carb.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

carb.model.fig <- ggplot(T90.df.carb.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.carb, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.carb, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(calab)+
  xlab("")+
  geom_point(aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r lipid model, echo=FALSE}

# subsetting
T90.df.lipid <- subset(T90.df, param=="lipid")
T0.df.lipid <- subset(T0.df.a, param=="lipid")
T90.df.lipid <- completeFun(T90.df.lipid, "value") # run function to remove any missing values from "rate"
#
## mixed effect model run using lmer()
#T90.lipid.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.lipid)
#out <- simulate(T90.lipid.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.lipid),re.form=NA))
#boots <- cbind(predict(T90.lipid.model,re.form=NA), boots)
#T90.df.lipid.a <- (cbind(T90.df.lipid, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.lipid.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#
#lipid.df <- paste("lipid_model_T90", date, sep="_") 
#lipid.df <- paste(lipid.df, ".csv", sep="") 
#write.csv(T90.df.lipid.a, file=lipid.df)  

```

```{r lipid figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

T90.df.lipid.a <- read.csv("lipid_model_T90_2019-11-20.csv", head=T)
T90.df.lipid.a$ftemp <- as.factor(T90.df.lipid.a$ftemp)
T90.df.lipid.a$fpco2 <- as.factor(T90.df.lipid.a$fpco2)
T90.df.lipid.a$species <- factor(T90.df.lipid.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

lipid.model.fig <- ggplot(T90.df.lipid.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.lipid, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.lipid, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(llab)+
  xlab("")+
  geom_point(aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r denisty model, echo=FALSE, message=FALSE}

# subsetting
T90.df.den <- subset(T90.df, param=="den")
T0.df.den <- subset(T0.df.a, param=="den")
T90.df.den <- completeFun(T90.df.den, "value") # run function to remove any missing values from "rate"
#
## mixed effect model run using lmer()
#T90.den.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.den)
#out <- simulate(T90.den.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.den),re.form=NA))
#boots <- cbind(predict(T90.den.model,re.form=NA), boots)
#T90.df.den.a <- (cbind(T90.df.den, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.den.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#den.df <- paste("density_model_T90", date, sep="_") 
#den.df <- paste(den.df, ".csv", sep="") 
#write.csv(T90.df.den.a, file=den.df)  

```

```{r denisty figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

T90.df.den.a <- read.csv("density_model_T90_2019-11-21.csv", head=T)
T90.df.den.a$ftemp <- as.factor(T90.df.den.a$ftemp)
T90.df.den.a$fpco2 <- as.factor(T90.df.den.a$fpco2)
T90.df.den.a$species <- factor(T90.df.den.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

den.model.fig <- ggplot(T90.df.den.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(),  panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.den, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.den, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(dlab)+
  xlab("")+
  geom_point(aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r chlorophyll model, echo=FALSE, message=FALSE}

# subsetting
T90.df.chla <- subset(T90.df, param=="chla")
T0.df.chla <- subset(T0.df.a, param=="chla")
T90.df.chla <- completeFun(T90.df.chla, "value") # run function to remove any missing values from "rate"
#
## mixed effect model run using lmer()
#T90.chla.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.chla)
#out <- simulate(T90.chla.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=T, data = T90.df.chla),re.form=NA))
#boots <- cbind(predict(T90.chla.model,re.form=NA), boots)
#T90.df.chla.a <- (cbind(T90.df.chla, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.chla.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#chla.df <- paste("chlorophyll_model_T90", date, sep="_") 
#chla.df <- paste(chla.df, ".csv", sep="") 
#write.csv(T90.df.chla.a, file=chla.df)  

```

```{r chlorophyll figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}
T90.df.chla.a <- read.csv("chlorophyll_model_T90_2019-11-21.csv", head=T)
T90.df.chla.a$ftemp <- as.factor(T90.df.chla.a$ftemp)
T90.df.chla.a$fpco2 <- as.factor(T90.df.chla.a$fpco2)
T90.df.chla.a$species <- factor(T90.df.chla.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

chla.model.fig <- ggplot(T90.df.chla.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.chla, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.chla, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(clab)+
  xlab("")+
  geom_point(aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

## Figures:

### Figure 1

```{r figure 2, echo=FALSE, fig.height = 14, fig.width = 10, fig.align = "center", results = 'hide'}

# full T90 plot with coral images

full.T90.model.fig <- plot_grid(corals, pro.model.fig, lipid.model.fig, carb.model.fig, den.model.fig, chla.model.fig, labels=c("", "A", "B", "C", "D", "E"), ncol = 1, align = "v", axis = 'lb', rel_heights = c(1,1,1,1,1,1), scale = 0.9)
#full.T90.model.fig

## make interactive Rmarkdown version
#full.T90.fig.interactive <- subplot(pro.model.fig, lipid.model.fig, carb.model.fig, #den.model.fig, chla.model.fig, nrows = 6)
#
#full.T90.fig.interactive

```

Modelled 95% confidence interval of (A) total protein (mg/cm2), (B) total lipid (mg/cm2), (C) total carbohydrate (mg/cm2), (D) cell density (10^6 cells/cm2), and (E) Chlorophyll a (ug/cm2) for each coral species, with individual coral fragment physiology denoted by points. Blue denotes 28C and red denotes 31C, with *p*CO2 treatment along the x axis.

<br/>
<br/>

### Figure 2

```{r host phys model, echo=FALSE, message=FALSE}

# subsetting
T90.df.host <- subset(T90.df, param=="host")
T0.df.host <- subset(T0.df.a, param=="host")
T90.df.host <- completeFun(T90.df.host, "value") # run function to remove any missing values from "rate"
#
## mixed effect model run using lmer()
#T90.host.model <- lmer(value ~ species * ftemp + fpco2 + (1 | colony), REML=T, data = T90.df.host)
#out <- simulate(T90.host.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * ftemp + fpco2 + (1 | colony), REML=T, data = T90.df.host),re.form=NA))
#boots <- cbind(predict(T90.host.model,re.form=NA), boots)
#T90.df.host.a <- (cbind(T90.df.host, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.host.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#host.df <- paste("host_model_T90", date, sep="_") 
#host.df <- paste(host.df, ".csv", sep="") 
#write.csv(T90.df.host.a, file=host.df)  

```

```{r host phys figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

T90.df.host.a <- read.csv("host_model_T90_2019-11-21.csv", head=T)
T90.df.host.a$ftemp <- as.factor(T90.df.host.a$ftemp)
T90.df.host.a$species <- factor(T90.df.host.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

host.model.fig <- ggplot(data=T90.df.host.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.host, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.host, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab("Total host energy \n reserves (mg cm )")+
  xlab("")+
  geom_point( aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species, ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r symb phys model, echo=FALSE, message=FALSE}

# subsetting
T90.df.symb <- subset(T90.df, param=="symb")
T0.df.symb <- subset(T0.df.a, param=="symb")
T90.df.symb$value[T90.df.symb$value > 4000] <- NA
T90.df.symb <- completeFun(T90.df.symb, "value") # run function to remove any missing values from "rate"

## mixed effect model run using
#T90.symb.model <- lmer(value ~ species * ftemp * fpco2 + reef + (1 | colony), REML=TRUE, data = T90.df.symb)
#out <- simulate(T90.symb.model,nsim=bootnum,seed=seed,re.form=NULL)
#boots <- apply(out,2,function(x) predict(lmer(x ~ species * ftemp * fpco2 + reef + (1 | colony), REML=T, data = T90.df.symb), re.form=NA))
#boots <- cbind(predict(T90.symb.model,re.form=NA), boots)
#T90.df.symb.a <- (cbind(T90.df.symb, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
#colnames(T90.df.symb.a)[17:19] <- c("mean", "lowerci", "upperci")
#
#symb.df <- paste("symb_model_T90", date, sep="_") 
#symb.df <- paste(symb.df, ".csv", sep="") 
#write.csv(T90.df.symb.a, file=symb.df)  

```

```{r symb phys figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE, include=FALSE}

T90.df.symb.a <- read.csv("symb_model_T90_2019-11-21.csv", head=T)
T90.df.symb.a$ftemp <- as.factor(T90.df.symb.a$ftemp)
T90.df.symb.a$species <- factor(T90.df.symb.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

symb.model.fig <- ggplot(data=T90.df.symb.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  geom_point(data=T0.df.symb, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  geom_linerange(data=T0.df.symb, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+ 
  #geom_point(data=df.comp.symb, aes(x=treat, y=(value*1000000), group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=comp.sum.symb, aes(x=treat, ymin=(value*10000000)-(ci*10000000), ymax=(value*10000000)+(ci*10000000)), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab("Chlorophyll a \n per symbiont cell")+
  xlab("")+
  geom_point( aes(treat, value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x=treat, ymin=lowerci, ymax=upperci, colour=ftemp), position = dodge, size = 1)+
  #geom_point(aes(x=treat, y=mean), position = dodge, size = 3, colour="black")+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00"))+
  facet_wrap(~species,  ncol=4, scales="free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r figure 3, echo=FALSE, fig.height = 4.6, fig.width = 10, fig.align = "center", results = 'hide'}

host.symb.T90.model.fig <- plot_grid(host.model.fig, symb.model.fig, labels = c("A", "B"), ncol = 1, align = "v", axis = 'lb')

host.symb.T90.model.fig

```
Modelled 95% confidence interval of (A) total host energy reserves (mg/cm2) and (B) chlorophyll a per symbiont cell (ug/10^6 cells) for *S. siderea*, *P. strigosa*, *P. astreoides*, and *U. tenuifolia* for each coral species, with individual coral fragment physiology denoted by points. Blue denotes 28C and red denotes 31C, with *p*CO2 treatment along the x axis.







## Tables:

```{r T0 table, echo=FALSE}

T0.tab <- T0.df.a[,c(9,16,18:20)]
T0.tab$binder <- paste(T0.tab$species, T0.tab$param, sep = "_")

T0.mean <- summarySE(data=T0.tab, measurevar = "mean", groupvars = c("species", "param", "binder"))
T0.low <- summarySE(data=T0.tab, measurevar = "lowerci", groupvars = c("species", "param", "binder"))
T0.up <- summarySE(data=T0.tab, measurevar = "upperci", groupvars = c("species", "param", "binder"))

T0.tab <- cbind(T0.mean, T0.low, T0.up)[, -c(1,3,6:12, 14:20, 22:24)]
T0.tab$mean <- round(T0.tab$mean, 2)
T0.tab$lowerci <- round(T0.tab$lowerci, 2)
T0.tab$upperci <- round(T0.tab$upperci, 2)

colnames(T0.tab)[colnames(T0.tab)=="param"] <- "parameter"
colnames(T0.tab)[colnames(T0.tab)=="lowerci"] <- "lower 95%"
colnames(T0.tab)[colnames(T0.tab)=="upperci"] <- "upper 95%"

table1 <- kable(T0.tab, booktabs = T, caption = "Table 1. T0 modelled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F, position="center") %>% 
  pack_rows("(a) SSID", 1, 7) %>%
  pack_rows("(b) PSTR", 8, 14) %>%
  pack_rows("(c) PAST", 15, 21) %>%
  pack_rows("(d) UTEN", 22, 28)
table1

```

```{r protein table, echo=FALSE}

T90.pro.tab <- T90.df.pro.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
T90.pro.tab$binder <- paste(T90.pro.tab$species, T90.pro.tab$treat2, sep = "_")

T90.pro.mean <- summarySE(data=T90.pro.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.pro.low <- summarySE(data=T90.pro.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.pro.up <- summarySE(data=T90.pro.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

T90.pro.tab <- cbind(T90.pro.mean, T90.pro.low, T90.pro.up)[, c(2,4,5,13,21)]
T90.pro.tab$mean <- round(T90.pro.tab$mean, 2)
T90.pro.tab$lowerci <- round(T90.pro.tab$lowerci, 2)
T90.pro.tab$upperci <- round(T90.pro.tab$upperci, 2)

colnames(T90.pro.tab)[colnames(T90.pro.tab)=="treat2"] <- "treatment"
colnames(T90.pro.tab)[colnames(T90.pro.tab)=="lowerci"] <- "lower 95%"
colnames(T90.pro.tab)[colnames(T90.pro.tab)=="upperci"] <- "upper 95%"
T90.pro.tab$treatment <- factor(T90.pro.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table2 <- kable(T90.pro.tab, booktabs = T, caption = "Table 2. T90 modelled mean coral host protein content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table2

```

```{r lipid table, echo=FALSE}

T90.lipid.tab <- T90.df.lipid.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
T90.lipid.tab$binder <- paste(T90.lipid.tab$species, T90.lipid.tab$treat2, sep = "_")

T90.lipid.mean <- summarySE(data=T90.lipid.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.lipid.low <- summarySE(data=T90.lipid.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.lipid.up <- summarySE(data=T90.lipid.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

T90.lipid.tab <- cbind(T90.lipid.mean, T90.lipid.low, T90.lipid.up)[, c(2,4,5,13,21)]
T90.lipid.tab$mean <- round(T90.lipid.tab$mean, 2)
T90.lipid.tab$lowerci <- round(T90.lipid.tab$lowerci, 2)
T90.lipid.tab$upperci <- round(T90.lipid.tab$upperci, 2)

colnames(T90.lipid.tab)[colnames(T90.lipid.tab)=="treat2"] <- "treatment"
colnames(T90.lipid.tab)[colnames(T90.lipid.tab)=="lowerci"] <- "lower 95%"
colnames(T90.lipid.tab)[colnames(T90.lipid.tab)=="upperci"] <- "upper 95%"
T90.lipid.tab$treatment <- factor(T90.lipid.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table3 <- kable(T90.lipid.tab, booktabs = T, caption = "Table 3. T90 modelled mean coral host lipid content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table3

```

```{r carbohydrate table, echo=FALSE}

T90.carb.tab <- T90.df.carb.a[,c(10,18,19:21)] #subset for species, treatment, and model values
T90.carb.tab$binder <- paste(T90.carb.tab$species, T90.carb.tab$treat2, sep = "_")

T90.carb.mean <- summarySE(data=T90.carb.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.carb.low <- summarySE(data=T90.carb.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.carb.up <- summarySE(data=T90.carb.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

T90.carb.tab <- cbind(T90.carb.mean, T90.carb.low, T90.carb.up)[, c(2,4,5,13,21)]
T90.carb.tab$mean <- round(T90.carb.tab$mean, 2)
T90.carb.tab$lowerci <- round(T90.carb.tab$lowerci, 2)
T90.carb.tab$upperci <- round(T90.carb.tab$upperci, 2)

colnames(T90.carb.tab)[colnames(T90.carb.tab)=="treat2"] <- "treatment"
colnames(T90.carb.tab)[colnames(T90.carb.tab)=="lowerci"] <- "lower 95%"
colnames(T90.carb.tab)[colnames(T90.carb.tab)=="upperci"] <- "upper 95%"
T90.carb.tab$treatment <- factor(T90.carb.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table4 <- kable(T90.carb.tab, booktabs = T, caption = "Table 4. T90 modelled mean coral host carbohydrate content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table4

```

```{r density table, echo=FALSE}

T90.den.tab <- T90.df.den.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
T90.den.tab$binder <- paste(T90.den.tab$species, T90.den.tab$treat2, sep = "_")

T90.den.mean <- summarySE(data=T90.den.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.den.low <- summarySE(data=T90.den.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.den.up <- summarySE(data=T90.den.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

T90.den.tab <- cbind(T90.den.mean, T90.den.low, T90.den.up)[, c(2,4,5,13,21)]
T90.den.tab$mean <- round(T90.den.tab$mean, 2)
T90.den.tab$lowerci <- round(T90.den.tab$lowerci, 2)
T90.den.tab$upperci <- round(T90.den.tab$upperci, 2)

colnames(T90.den.tab)[colnames(T90.den.tab)=="treat2"] <- "treatment"
colnames(T90.den.tab)[colnames(T90.den.tab)=="lowerci"] <- "lower 95%"
colnames(T90.den.tab)[colnames(T90.den.tab)=="upperci"] <- "upper 95%"
T90.den.tab$treatment <- factor(T90.den.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table5 <- kable(T90.den.tab, booktabs = T, caption = "Table 5. T90 modelled mean algal endosymbiont cell density and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table5

```

```{r chlorophyll table, echo=FALSE}

T90.chla.tab <- T90.df.chla.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
T90.chla.tab$binder <- paste(T90.chla.tab$species, T90.chla.tab$treat2, sep = "_")

T90.chla.mean <- summarySE(data=T90.chla.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.chla.low <- summarySE(data=T90.chla.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.chla.up <- summarySE(data=T90.chla.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

T90.chla.tab <- cbind(T90.chla.mean, T90.chla.low, T90.chla.up)[, c(2,4,5,13,21)]
T90.chla.tab$mean <- round(T90.chla.tab$mean, 2)
T90.chla.tab$lowerci <- round(T90.chla.tab$lowerci, 2)
T90.chla.tab$upperci <- round(T90.chla.tab$upperci, 2)

colnames(T90.chla.tab)[colnames(T90.chla.tab)=="treat2"] <- "treatment"
colnames(T90.chla.tab)[colnames(T90.chla.tab)=="lowerci"] <- "lower 95%"
colnames(T90.chla.tab)[colnames(T90.chla.tab)=="upperci"] <- "upper 95%"
T90.chla.tab$treatment <- factor(T90.chla.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table6 <- kable(T90.chla.tab, booktabs = T, caption = "Table 6. T90 modelled mean algal endosymbiont chlorophyll a content and 95% confichlace intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table6

```

```{r host table, echo=FALSE}

T90.host.tab <- T90.df.host.a[,c(9,15,16,18:20)] #subset for species, treatment, parameter, and model values
T90.host.tab$binder <- paste(T90.host.tab$species, T90.host.tab$param, T90.host.tab$treat2, sep = "_")

T90.host.mean <- summarySE(data=T90.host.tab, measurevar = "mean", groupvars = c("species", "param", "treat2", "binder"))
T90.host.low <- summarySE(data=T90.host.tab, measurevar = "lowerci", groupvars = c("species", "param", "treat2", "binder"))
T90.host.up <- summarySE(data=T90.host.tab, measurevar = "upperci", groupvars = c("species", "param", "treat2", "binder"))

T90.host.tab <- cbind(T90.host.mean, T90.host.low, T90.host.up)[, c(3,5,6,15,24)]
T90.host.tab$mean <- round(T90.host.tab$mean, 2)
T90.host.tab$lowerci <- round(T90.host.tab$lowerci, 2)
T90.host.tab$upperci <- round(T90.host.tab$upperci, 2)

colnames(T90.host.tab)[colnames(T90.host.tab)=="treat2"] <- "treatment"
colnames(T90.host.tab)[colnames(T90.host.tab)=="lowerci"] <- "lower 95%"
colnames(T90.host.tab)[colnames(T90.host.tab)=="upperci"] <- "upper 95%"
T90.host.tab$treatment <- factor(T90.host.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table8 <- kable(T90.host.tab, booktabs = T, caption = "Table 8. Total coral host physiology at T90 modelled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table8

```

```{r symbiont table, echo=FALSE}

T90.symb.tab <- T90.df.symb.a[,c(9,15,16,18:20)] #subset for species, treatment, parameter, and model values
T90.symb.tab$binder <- paste(T90.symb.tab$species, T90.symb.tab$param, T90.symb.tab$treat2, sep = "_")

T90.symb.mean <- summarySE(data=T90.symb.tab, measurevar = "mean", groupvars = c("species", "param", "treat2", "binder"))
T90.symb.low <- summarySE(data=T90.symb.tab, measurevar = "lowerci", groupvars = c("species", "param", "treat2", "binder"))
T90.symb.up <- summarySE(data=T90.symb.tab, measurevar = "upperci", groupvars = c("species", "param", "treat2", "binder"))

T90.symb.tab <- cbind(T90.symb.mean, T90.symb.low, T90.symb.up)[, c(3,5,6,15,24)]
T90.symb.tab$mean <- round(T90.symb.tab$mean, 2)
T90.symb.tab$lowerci <- round(T90.symb.tab$lowerci, 2)
T90.symb.tab$upperci <- round(T90.symb.tab$upperci, 2)

colnames(T90.symb.tab)[colnames(T90.symb.tab)=="treat2"] <- "treatment"
colnames(T90.symb.tab)[colnames(T90.symb.tab)=="lowerci"] <- "lower 95%"
colnames(T90.symb.tab)[colnames(T90.symb.tab)=="upperci"] <- "upper 95%"
T90.symb.tab$treatment <- factor(T90.symb.tab$treatment, c("288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table9 <- kable(T90.symb.tab, booktabs = T, caption = "Table 9. Total algal endosymbiont physiology at T90 modelled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 8) %>%
  pack_rows("(b) PSTR", 9, 16) %>%
  pack_rows("(c) PAST", 17, 24) %>%
  pack_rows("(d) UTEN", 25, 30)
table9

```

<br/>
<br/>

```{r}
sessionInfo()
```

