---
title: "Chapter 3: Physiology"
author: "Colleen Bove"
date: "17 December 2019"
output: 
  word_document:
    reference_docx: word_syles_reference_1.docx
always_allow_html: true
---
# Results

#### (A) Coral host and algal endosymbiont physiology
> Coral host total tissue energy reserves (mg cm^-2^) was calculated as the sum of each protein, lipid, and carbohydrate value per coral host. Total host energy reserves of *P. astreoides* at T0 were clearly greater than the total energy reserves quantified in coral hosts maintained under at control treatment at T90 (**Figure 1A**). There was no difference in total energy reserves between T0 and T90 control coral hosts in either *S. siderea* or *P. strigosa*. Elevated temperature (31&deg;C) resulted in a clear reduction in total coral host energy reserves in only *P. strigosa* across all pCO2 treatments (**Figure 1A**). No overall effect of *p*CO~2~ was quantified in any of the four species examined. 

> Algal endosymbiont cell density (10^6^ cells cm^-2^) in *P. astreoides* T0 densities were clearly lower than those measured under all treatments at T90 (**Figure 1B**). Algal endosymbiont cell densities did not exhibit a statistically clear difference between T0 fragments and T90 fragments maintained at the control treatment in *S. siderea* or *P. strigosa*. Neither *p*CO~2~ nor temperature exhibited a statistically clear overall effect on algal endosymbiont cell densities quantified at T90 in any of the three coral species (**Figure 1B**). Algal endosymbiont chlorophyll a content (ug cm^-2^) of *S. siderea* and *P. strigosa* at T0 was lower than the measured chlorophyll a in fragments maintained in the control treatment at T90 (**Figure 1C**). Conversely, chlorophyll a measured at T0 was not clearly different than in fragments reared in the control treatment at T90 for *P. astreoides*. All species exhibited reduced algal endosymbiont chlorophyll a in the highest *p*CO~2~ treatment, while elevated temperature (31&deg;C) only clearly reduces chlorophyll a in the algal endosymbionts associated with *P. strigosa* (**Figure 1C**).


#### (B) Host transcriptomic responses
> I will talk about HOST trends/findings about gene expression here.


#### (C) Algal endosymbiont transcriptomic responses
> I will talk about symbiont trends/findings about gene expression here.


#### (D) Overall physiological response
> This will discuss overall responses and the WGCNA here.


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)

```

```{r packages, include=FALSE}

#Packages to load
library("knitr")
library("readr")
library("ggplot2")
library("dplyr")
library("tidyr")
library("openxlsx")
library("plotly")
library("tidyverse")
library("shiny")
library("Rmisc")
library("cowplot")
library("ggfortify")
library("kableExtra")
library("readr")
library("lme4")
library("magick")

```

```{r labels, include=FALSE}

#Set some standards and units
#dodge width
dodge=position_dodge(width=0.3)
dodge2=position_dodge(width = 0.6)
jitter=position_jitter(width=0.1)

theme_set(theme_classic())

# set parameter labels
Tlab<-"Temperature (°C)"
alab<-expression(paste(italic("p"),"CO" [2]~ "("*mu,'atm)'))
dlab<-expression(paste("Cell density (10"^6,"cells cm"^-2,")"))
plab<-expression(paste("Total protein (mg cm"^-2,")"))
calab<-expression(paste("Carbohydrate (mg cm"^-2,")"))
clab<-expression(paste("Chlorophyll a ("*mu,"g cm"^-2,")"))
rlab<-expression(paste("Calcification rate (mg cm"^-2~"day"^-1,")"))
llab<-expression(paste("Total Lipid (mg cm"^-2,")"))
date <- Sys.Date() 

```

```{r initial dataframe, include=FALSE}

df <- read_csv("phys_all_21Oct19.csv")

df$X1 <- NULL
df$X1_1 <- NULL
names(df)[38]<-"carb"
names(df)[39]<-"lipid"
df$ftemp <- as.factor(df$ftemp)
df$fpco2 <- as.factor(df$fpco2)
df$colony <- as.factor(df$colony)
df$species <- factor(df$species, levels = c("S", "P", "A", "T"))
df$fpco2 <- gsub("2800", "3300", df$fpco2)
df$fpco2 <- gsub("280", "300", df$fpco2)
df$fpco2 <- gsub("400", "420", df$fpco2)
df$fpco2 <- gsub("700", "680", df$fpco2)
df$fpco2 <- factor(df$fpco2, c("420", "T0", "300", "680", "3300"))
df$ftemp <- factor(df$ftemp, c("28", "T0", "31"))
df$den <- df$den / 1000000
df$host <- df$pro + df$carb + df$lipid
df$treat[df$T0_T90 == "T0"] <- "T0"
df$treat <- factor(df$treat, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

# add a new treat column for plotting
df$treat2 <- df$treat
df$treat <- gsub("T0", 2, df$treat)
df$treat <- gsub("288_28", 4, df$treat)
df$treat <- gsub("311_31", 4, df$treat)
df$treat <- gsub("447_28", 6, df$treat)
df$treat <- gsub("405_31", 6, df$treat)
df$treat <- gsub("673_28", 8, df$treat)
df$treat <- gsub("701_31", 8, df$treat)
df$treat <- gsub("3285_28", 10, df$treat)
df$treat <- gsub("3309_31", 10, df$treat)

df$treat <- as.numeric(df$treat) #convert 'treat' column to numerics

```


```{r bootstrap model setup, echo=FALSE}

# this function remove rows with any missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

### Performing the parametric bootstrapping of the model:
bootnum = 2000 # set number of iterations (we used 2000) between 999 and 9999
seed = 7 #seed to make results replicatable (our seed was 7)

```

```{r coral images, echo=FALSE}

# make cowplot of all coral images
s <- cowplot::ggdraw() + cowplot::draw_image("SSID.png", scale = 0.9) 
p <- cowplot::ggdraw() + cowplot::draw_image("PSTR.png", scale = 0.9)
a <- cowplot::ggdraw() + cowplot::draw_image("PAST.png", scale = 0.9)
#u <- cowplot::ggdraw() + cowplot::draw_image("UTEN.png", scale = 0.9)
corals <- cowplot::plot_grid(s, p, a, ncol = 3, scale=0.7)

```

```{r T90 df, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

#modify dataframe for T90 samples
df2 <- df[,c(1:16,38:41)]
df2 <- gather(df2, param, value, den:host) # make column of parameter and value
df2$param <- factor(df2$param, levels = c("pro", "carb", "lipid", "den", "chla", "host"))
df2$species <- revalue(x = df2$species, c("S" = "SSID", "P" = "PSTR", "A" = "PAST", "T" = "UTEN"))
df2 <- subset(df2, species != "UTEN")

```



```{r protein model, eval=FALSE, include=FALSE}

# subsetting
df2.pro <- subset(df2, param=="pro")
df2.pro <- completeFun(df2.pro, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.pro.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.pro)
out <- simulate(T90.pro.model, nsim=bootnum, seed=seed, re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.pro),re.form=NA))
boots <- cbind(predict(T90.pro.model,re.form=NA), boots)
df2.pro.a <- (cbind(df2.pro, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.pro.a)[17:19] <- c("mean", "lowerci", "upperci")

pro.df <- paste("Protein_model", date, sep="_") 
pro.df <- paste(pro.df, ".csv", sep="") 
write.csv(df2.pro.a, file=pro.df)  

```

```{r protein figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

df2.pro.a <- read.csv("Protein_model_2019-12-17.csv", head=T)
df2.pro.a$ftemp <- as.factor(df2.pro.a$ftemp)
df2.pro.a$fpco2 <- as.factor(df2.pro.a$fpco2)
df2.pro.a$species <- factor(df2.pro.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

pro.model.fig <- ggplot(df2.pro.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  #scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  scale_x_continuous(breaks = df2.pro.a$treat, labels = df2.pro.a$fpco2)+
  #geom_point(data=T0.df.pro, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.pro, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(plab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))  

```

```{r carb model, eval=FALSE, include=FALSE}

# subsetting
df2.carb <- subset(df2, param=="carb")
df2.carb <- completeFun(df2.carb, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.carb.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.carb)
out <- simulate(T90.carb.model,nsim=bootnum,seed=seed,re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.carb),re.form=NA))
boots <- cbind(predict(T90.carb.model,re.form=NA), boots)
df2.carb.a <- (cbind(df2.carb, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.carb.a)[17:19] <- c("mean", "lowerci", "upperci")

carb.df <- paste("carbohydrate_model", date, sep="_") 
carb.df <- paste(carb.df, ".csv", sep="") 
write.csv(df2.carb.a, file=carb.df)  

```

```{r carb figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

df2.carb.a <- read.csv("carbohydrate_model_2019-12-17.csv", head=T)
df2.carb.a$ftemp <- as.factor(df2.carb.a$ftemp)
df2.carb.a$fpco2 <- as.factor(df2.carb.a$fpco2)
df2.carb.a$species <- factor(df2.carb.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

carb.model.fig <- ggplot(df2.carb.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  #scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  scale_x_continuous(breaks = df2.carb.a$treat, labels = df2.carb.a$fpco2)+
  #geom_point(data=T0.df.carb, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.carb, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(calab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r lipid model, eval=FALSE, include=FALSE}

# subsetting
df2.lipid <- subset(df2, param=="lipid")
df2.lipid <- completeFun(df2.lipid, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.lipid.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.lipid)
out <- simulate(T90.lipid.model,nsim=bootnum,seed=seed,re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.lipid),re.form=NA))
boots <- cbind(predict(T90.lipid.model,re.form=NA), boots)
df2.lipid.a <- (cbind(df2.lipid, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.lipid.a)[17:19] <- c("mean", "lowerci", "upperci")

lipid.df <- paste("lipid_model", date, sep="_") 
lipid.df <- paste(lipid.df, ".csv", sep="") 
write.csv(df2.lipid.a, file=lipid.df)  

```

```{r lipid figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

df2.lipid.a <- read.csv("lipid_model_2019-12-17.csv", head=T)
df2.lipid.a$ftemp <- as.factor(df2.lipid.a$ftemp)
df2.lipid.a$fpco2 <- as.factor(df2.lipid.a$fpco2)
df2.lipid.a$species <- factor(df2.lipid.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

lipid.model.fig <- ggplot(df2.lipid.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  #scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  scale_x_continuous(breaks = df2.lipid.a$treat, labels = df2.lipid.a$fpco2)+
  #geom_point(data=T0.df.lipid, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.lipid, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(llab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r denisty model, eval=FALSE, message=FALSE, include=FALSE}

# subsetting
df2.den <- subset(df2, param=="den")
df2.den <- completeFun(df2.den, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.den.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.den)
out <- simulate(T90.den.model,nsim=bootnum,seed=seed,re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.den),re.form=NA))
boots <- cbind(predict(T90.den.model,re.form=NA), boots)
df2.den.a <- (cbind(df2.den, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.den.a)[17:19] <- c("mean", "lowerci", "upperci")

den.df <- paste("density_model", date, sep="_") 
den.df <- paste(den.df, ".csv", sep="") 
write.csv(df2.den.a, file=den.df)  

```

```{r denisty figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

df2.den.a <- read.csv("density_model_2019-12-17.csv", head=T)
df2.den.a$ftemp <- as.factor(df2.den.a$ftemp)
df2.den.a$fpco2 <- as.factor(df2.den.a$fpco2)
df2.den.a$species <- factor(df2.den.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

den.model.fig <- ggplot(df2.den.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  #scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  scale_x_continuous(breaks = df2.den.a$treat, labels = df2.den.a$fpco2)+
  #geom_point(data=T0.df.den, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.den, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(dlab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")


  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```

```{r chlorophyll model, eval=FALSE, message=FALSE, include=FALSE}

# subsetting
df2.chla <- subset(df2, param=="chla")
df2.chla <- completeFun(df2.chla, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.chla.model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.chla)
out <- simulate(T90.chla.model,nsim=bootnum,seed=seed,re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML=TRUE, data = df2.chla),re.form=NA))
boots <- cbind(predict(T90.chla.model,re.form=NA), boots)
df2.chla.a <- (cbind(df2.chla, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.chla.a)[17:19] <- c("mean", "lowerci", "upperci")

chla.df <- paste("chlorophyll_model", date, sep="_") 
chla.df <- paste(chla.df, ".csv", sep="") 
write.csv(df2.chla.a, file=chla.df)  

```

```{r chlorophyll figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}
df2.chla.a <- read.csv("chlorophyll_model_2019-12-17.csv", head=T)
df2.chla.a$ftemp <- as.factor(df2.chla.a$ftemp)
df2.chla.a$fpco2 <- as.factor(df2.chla.a$fpco2)
df2.chla.a$species <- factor(df2.chla.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

chla.model.fig <- ggplot(df2.chla.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  scale_x_continuous(breaks = df2.chla.a$treat, labels = df2.chla.a$fpco2)+
  #geom_point(data=T0.df.chla, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.chla, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab(clab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```



```{r host phys model, eval=FALSE, message=FALSE, include=FALSE}

# subsetting
df2.host <- subset(df2, param=="host")
df2.host <- completeFun(df2.host, "value") # run function to remove any missing values

## mixed effect model run using lmer()
T90.host.model <- lmer(value ~ species * (ftemp + fpco2) + (1 | colony), REML=TRUE, data = df2.host)
out <- simulate(T90.host.model,nsim=bootnum,seed=seed,re.form=NULL)
boots <- apply(out,2,function(x) predict(lmer(x ~ species * ftemp + fpco2 + (1 | colony), REML=TRUE, data = df2.host),re.form=NA))
boots <- cbind(predict(T90.host.model,re.form=NA), boots)
df2.host.a <- (cbind(df2.host, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975))))))))
colnames(df2.host.a)[17:19] <- c("mean", "lowerci", "upperci")

host.df <- paste("host_model", date, sep="_") 
host.df <- paste(host.df, ".csv", sep="") 
write.csv(df2.host.a, file=host.df)  

```

```{r host phys figure, echo=FALSE, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

df2.host.a <- read.csv("host_model_2019-12-17.csv", head=T)
df2.host.a$ftemp <- as.factor(df2.host.a$ftemp)
df2.host.a$species <- factor(df2.host.a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

host.model.fig <-ggplot(df2.host.a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  #scale_x_discrete(limits=c(2, 4, 6, 8, 10))+
  scale_x_continuous(breaks = df2.host.a$treat, labels = df2.host.a$fpco2)+
  #geom_point(data=T0.df.host, aes(x=treat, y=value, group = species), alpha = 0.3, size = 2, shape = 8, colour = "#009E73")+
  #geom_linerange(data=T0.df.host, aes(x=treat, ymin=lowerci, ymax=upperci), size = 1, colour = "#009E73")+
  geom_vline(xintercept = 3)+
  ylab("Total host energy \n reserves (mg cm-2)")+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y")
  #theme(panel.background = element_rect(fill = "lightgrey", colour = "lightgrey", size = 0.5, linetype = "solid"), plot.background = element_rect(fill = "lightgrey"))

```


```{r figure 3, echo=FALSE, fig.height = 10, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

fig1 <- plot_grid(corals, host.model.fig, den.model.fig, chla.model.fig, labels = c("", "A", "B", "C"), ncol = 1, align = "v", axis = 'lb')
fig1

ggsave("Fig1_physiology_18Dec19.pdf")

```
<br/>
**Figure 1.** Modeled 95% confidence interval of (**A**) total host energy reserves (mg cm^-2^), (**B**) cell density (10^6^ cells cm^-2^), and (**C**) Chlorophyll a (ug cm^-2^) for *S. siderea*, *P. strigosa*, and *P. astreoides* at T0 (green) or T90 (red/blue), with individual coral fragment physiology denoted by points. Blue denotes 28&deg;C and red denotes 31&deg;C, with *p*CO~2~ treatment along the x axis.



```{r protein table, include=FALSE}

pro.tab <- df2.pro.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
pro.tab$binder <- paste(pro.tab$species, pro.tab$treat2, sep = "_")

T90.pro.mean <- summarySE(data=pro.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.pro.low <- summarySE(data=pro.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.pro.up <- summarySE(data=pro.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

pro.tab <- cbind(T90.pro.mean, T90.pro.low, T90.pro.up)[, c(1,2,4,5,13,21)]
pro.tab$mean <- round(pro.tab$mean, 2)
pro.tab$lowerci <- round(pro.tab$lowerci, 2)
pro.tab$upperci <- round(pro.tab$upperci, 2)

colnames(pro.tab)[colnames(pro.tab)=="treat2"] <- "treatment"
colnames(pro.tab)[colnames(pro.tab)=="lowerci"] <- "lower 95%"
colnames(pro.tab)[colnames(pro.tab)=="upperci"] <- "upper 95%"
pro.tab$treatment <- factor(pro.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table1 <- kable(pro.tab[,-c(1)], booktabs = T, caption = "Table 1. T90 modelled mean coral host protein content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table1

```

```{r lipid table, include=FALSE}

lipid.tab <- df2.lipid.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
lipid.tab$binder <- paste(lipid.tab$species, lipid.tab$treat2, sep = "_")

T90.lipid.mean <- summarySE(data=lipid.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.lipid.low <- summarySE(data=lipid.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.lipid.up <- summarySE(data=lipid.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

lipid.tab <- cbind(T90.lipid.mean, T90.lipid.low, T90.lipid.up)[, c(1,2,4,5,13,21)]
lipid.tab$mean <- round(lipid.tab$mean, 2)
lipid.tab$lowerci <- round(lipid.tab$lowerci, 2)
lipid.tab$upperci <- round(lipid.tab$upperci, 2)

colnames(lipid.tab)[colnames(lipid.tab)=="treat2"] <- "treatment"
colnames(lipid.tab)[colnames(lipid.tab)=="lowerci"] <- "lower 95%"
colnames(lipid.tab)[colnames(lipid.tab)=="upperci"] <- "upper 95%"
lipid.tab$treatment <- factor(lipid.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table2 <- kable(lipid.tab[,-c(1)], booktabs = T, caption = "Table 2. T90 modelled mean coral host lipid content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table2

```

```{r carbohydrate table, include=FALSE}

carb.tab <- df2.carb.a[,c(9,15,18:20)] #subset for species, treatment, and model values
carb.tab$binder <- paste(carb.tab$species, carb.tab$treat2, sep = "_")

T90.carb.mean <- summarySE(data=carb.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.carb.low <- summarySE(data=carb.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.carb.up <- summarySE(data=carb.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

carb.tab <- cbind(T90.carb.mean, T90.carb.low, T90.carb.up)[, c(1,2,4,5,13,21)]
carb.tab$mean <- round(carb.tab$mean, 2)
carb.tab$lowerci <- round(carb.tab$lowerci, 2)
carb.tab$upperci <- round(carb.tab$upperci, 2)

colnames(carb.tab)[colnames(carb.tab)=="treat2"] <- "treatment"
colnames(carb.tab)[colnames(carb.tab)=="lowerci"] <- "lower 95%"
colnames(carb.tab)[colnames(carb.tab)=="upperci"] <- "upper 95%"
carb.tab$treatment <- factor(carb.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table3 <- kable(carb.tab[,-c(1)], booktabs = T, caption = "Table 3. T90 modelled mean coral host carbohydrate content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table3

```

```{r density table, include=FALSE}

den.tab <- df2.den.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
den.tab$binder <- paste(den.tab$species, den.tab$treat2, sep = "_")

T90.den.mean <- summarySE(data=den.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.den.low <- summarySE(data=den.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.den.up <- summarySE(data=den.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

den.tab <- cbind(T90.den.mean, T90.den.low, T90.den.up)[, c(1,2,4,5,13,21)]
den.tab$mean <- round(den.tab$mean, 2)
den.tab$lowerci <- round(den.tab$lowerci, 2)
den.tab$upperci <- round(den.tab$upperci, 2)

colnames(den.tab)[colnames(den.tab)=="treat2"] <- "treatment"
colnames(den.tab)[colnames(den.tab)=="lowerci"] <- "lower 95%"
colnames(den.tab)[colnames(den.tab)=="upperci"] <- "upper 95%"
den.tab$treatment <- factor(den.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table4 <- kable(den.tab[,-c(1)], booktabs = T, caption = "Table 4. T90 modelled mean algal endosymbiont cell density and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table4

```

```{r chlorophyll table, include=FALSE}

chla.tab <- df2.chla.a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
chla.tab$binder <- paste(chla.tab$species, chla.tab$treat2, sep = "_")

T90.chla.mean <- summarySE(data=chla.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.chla.low <- summarySE(data=chla.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.chla.up <- summarySE(data=chla.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

chla.tab <- cbind(T90.chla.mean, T90.chla.low, T90.chla.up)[, c(1,2,4,5,13,21)]
chla.tab$mean <- round(chla.tab$mean, 2)
chla.tab$lowerci <- round(chla.tab$lowerci, 2)
chla.tab$upperci <- round(chla.tab$upperci, 2)

colnames(chla.tab)[colnames(chla.tab)=="treat2"] <- "treatment"
colnames(chla.tab)[colnames(chla.tab)=="lowerci"] <- "lower 95%"
colnames(chla.tab)[colnames(chla.tab)=="upperci"] <- "upper 95%"
chla.tab$treatment <- factor(chla.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table5 <- kable(chla.tab[,-c(1)], booktabs = T, caption = "Table 5. T90 modelled mean algal endosymbiont chlorophyll a content and 95% confichlace intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table5

```

```{r host table, include=FALSE}

host.tab <- df2.host.a[,c(9,15,16,18:20)] #subset for species, treatment, parameter, and model values
host.tab$binder <- paste(host.tab$species, host.tab$param, host.tab$treat2, sep = "_")

T90.host.mean <- summarySE(data=host.tab, measurevar = "mean", groupvars = c("species", "param", "treat2", "binder"))
T90.host.low <- summarySE(data=host.tab, measurevar = "lowerci", groupvars = c("species", "param", "treat2", "binder"))
T90.host.up <- summarySE(data=host.tab, measurevar = "upperci", groupvars = c("species", "param", "treat2", "binder"))

host.tab <- cbind(T90.host.mean, T90.host.low, T90.host.up)[, c(1,3,5,6,15,24)]
host.tab$mean <- round(host.tab$mean, 2)
host.tab$lowerci <- round(host.tab$lowerci, 2)
host.tab$upperci <- round(host.tab$upperci, 2)

colnames(host.tab)[colnames(host.tab)=="treat2"] <- "treatment"
colnames(host.tab)[colnames(host.tab)=="lowerci"] <- "lower 95%"
colnames(host.tab)[colnames(host.tab)=="upperci"] <- "upper 95%"
host.tab$treatment <- factor(host.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table6 <- kable(host.tab[,-c(1)], booktabs = T, caption = "Table 6. Total coral host physiology at T90 modelled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table6

```


```{r excel WB, include=FALSE}

### Create workbook
wb <- createWorkbook()

# add 'Table 1' worksheet
addWorksheet(wb, "Table 1 - protein") 
writeData(wb, sheet = 1, x = pro.tab)
setColWidths(wb, sheet = 1, cols = 1:5, widths = "auto")

# add 'Table 2' worksheet
addWorksheet(wb, "Table 2 - lipid") 
writeData(wb, sheet = 2, x = lipid.tab)
setColWidths(wb, sheet = 2, cols = 1:5, widths = "auto")

# add 'Table 3' worksheet
addWorksheet(wb, "Table 3 - carbohydrate") 
writeData(wb, sheet = 3, x = carb.tab)
setColWidths(wb, sheet = 3, cols = 1:5, widths = "auto")

# add 'Table 4' worksheet
addWorksheet(wb, "Table 4 - density") 
writeData(wb, sheet = 4, x = den.tab)
setColWidths(wb, sheet = 4, cols = 1:5, widths = "auto")

# add 'Table 5' worksheet
addWorksheet(wb, "Table 5 - chlorophyll") 
writeData(wb, sheet = 5, x = chla.tab)
setColWidths(wb, sheet = 5, cols = 1:5, widths = "auto")

# add 'Table 6' worksheet
addWorksheet(wb, "Table 6 - total host") 
writeData(wb, sheet = 6, x = host.tab)
setColWidths(wb, sheet = 6, cols = 1:5, widths = "auto")


# save workbook
saveWorkbook(wb, file="Ch3_Phys_tables.xlsx", overwrite = TRUE)


```

<br/>
<br/>

```{r}
sessionInfo()
```

