---
title: "Coral Holobiont Physiology under OA/OW "
output: 
  html_document:
    theme: simplex
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

<style>
  h2{color: teal !important}
  h1{color: navy !important}
  body{background-color: gray95 !important}
</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
options(warn = -1)

```

```{r packages, include=FALSE}

#library("devtools")
#install_github("vqv/ggbiplot") # need this to download ggbiplot if not already installed

## Packages to load
library(knitr)
library(readr)
library(ggplot2)
library(dplyr)
library(ggbiplot)
library(tidyr)
library(openxlsx)
library(plotly)
library(tidyverse)
library(vegan)
library(shiny)
library(Rmisc)
library(cowplot)
library(ggfortify)
library(kableExtra)
library(readr)
library(lmerTest)
library(vroom)
library(ggpubr)
library(magick)
library(Hmisc)
library(corrplot)
library(gridGraphics)
library(grid)
library(RColorBrewer)
library(wesanderson)

```

```{r set formatting and labels, include=FALSE}

## Set some standards and units

# dodge width
dodge=position_dodge(width=0.3)
dodge2=position_dodge(width = 0.6)
jitter=position_jitter(width=0.1)

# set figure theme
theme_set(theme_bw())

# set parameter labels
Tlab<-"Temperature (°C)"
alab<-expression(paste(italic("p"),"CO" [2]~ "("*mu,'atm)'))
dlab<-expression(paste("Cell density (10"^6,"cells cm"^-2,")"))
plab<-expression(paste("Total protein (mg cm"^-2,")"))
calab<-expression(paste("Carbohydrate (mg cm"^-2,")"))
clab<-expression(paste("Chlorophyll a ("*mu,"g cm"^-2,")"))
rlab<-expression(paste("Calcification rate (mg cm"^-2~"day"^-1,")"))
llab<-expression(paste("Total Lipid (mg cm"^-2,")"))
hlab<-expression(paste("Total Host (mg cm"^-2,")"))

# set the current date
date <- Sys.Date() 

```

```{r original dataframe adjustment, include=FALSE}

df <- read_csv("phys_all_21Oct19.csv") # read in full dataframe

# remove unnecessary column
df$X1 <- NULL
df$X1_1 <- NULL 

# rename a couple columns
names(df)[38]<-"carb"
names(df)[39]<-"lipid"
names(df)[17]<-"sum"
names(df)[34]<-"red" 

# set columns as factors
df$ftemp <- as.factor(df$ftemp)
df$fpco2 <- as.factor(df$fpco2)
df$colony <- as.factor(df$colony)
df$species <- factor(df$species, levels = c("S", "P", "A", "T")) # and reorder these

# replace some pCO2 values with ones we will use moving forward
df$fpco2 <- gsub("2800", "3300", df$fpco2)
df$fpco2 <- gsub("280", "300", df$fpco2)
df$fpco2 <- gsub("400", "420", df$fpco2)
df$fpco2 <- gsub("700", "680", df$fpco2)

# reorder factors for pCO2 and temp
df$fpco2 <- factor(df$fpco2, c("420", "T0", "300", "680", "3300"))
df$ftemp <- factor(df$ftemp, c("28", "T0", "31"))

# calculate phys parameters
df$den <- df$den / 1000000 # adjust symbiont density to display 10^6 cells
df$host <- df$pro + df$carb + df$lipid # calculate total host energy reserves (sum of carb, protein, lipids)
df$treat[df$T0_T90 == "T0"] <- "T0" # replace T0 'treat' with T0 text
df$treat <- factor(df$treat, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31")) # adjust treatment levels

# add a new treat column for plotting (replacing actual treatment with number for better plotting - see plot XX)
df$treat2 <- df$treat
df$treat <- gsub("T0", 2, df$treat)
df$treat <- gsub("288_28", 4, df$treat)
df$treat <- gsub("311_31", 4, df$treat)
df$treat <- gsub("447_28", 6, df$treat)
df$treat <- gsub("405_31", 6, df$treat)
df$treat <- gsub("673_28", 8, df$treat)
df$treat <- gsub("701_31", 8, df$treat)
df$treat <- gsub("3285_28", 10, df$treat)
df$treat <- gsub("3309_31", 10, df$treat)
df$treat <- as.numeric(df$treat) # convert 'treat' column to numerics (again, this is for plotting only)

# inverse of colours (so lower colour depicts more bleached coral)
df$sum <- (df$sum * -1)
df$red <- (df$red * -1)
df$blue_bw5 <- (df$blue_bw5 * -1)
df$green_bw5 <- (df$green_bw5 * -1)

## modify dataframe for simplified version
df2 <- df[,c(1:16, 38:40, 17, 34:36, 41)] # select columns of interest only
df2 <- gather(df2, param, value, den:blue_bw5) # make column of parameter and value
df2$param <- factor(df2$param, levels = c("pro", "carb", "lipid", "den", "chla", "host", "red", "green_bw5", "blue_bw5", "sum")) # reorder parameters
df2$species <- revalue(x = df2$species, c("S" = "SSID", "P" = "PSTR", "A" = "PAST", "T" = "UTEN")) # rename the species codes
df2 <- subset(df2, species != "UTEN") # remove UTEN (omitted due to high mortality in some treatments)

## remote T0 samples from dataframe for models
df2_T90 <- subset(df2, T0_T90 == "T90")

```

```{r bootstrap model setup}

## Function to remove rows with any missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

## Performing the parametric bootstrapping of the model:
bootnum = 2000 # set number of iterations (we used 2000) between 999 and 9999
seed = 7 #seed to make results replicatable (our seed was 7)

```

```{r coral images}

### I want to replace these images with field images taken of these species!!!

# make combination of all coral images
s <- cowplot::ggdraw() + cowplot::draw_image("SSID.png", scale = 0.9) 
p <- cowplot::ggdraw() + cowplot::draw_image("PSTR.png", scale = 0.9)
a <- cowplot::ggdraw() + cowplot::draw_image("PAST.png", scale = 0.9)
#u <- cowplot::ggdraw() + cowplot::draw_image("UTEN.png", scale = 0.9) # not including UTEN in the manuscript so it has been omitted 
corals <- cowplot::plot_grid(s, p, a, ncol = 3, scale=0.7) # final combination of species images

```

## Model selection for physiology{.tabset}

Physiological response parameters were assessed using mixed-effects linear models across species and treatments. Model selection was carried out using backward elimination of random-effects followed by fixed-effects using the package [*lmerTest*](https://cran.r-project.org/web/packages/lmerTest/lmerTest.pdf) (version `r packageVersion("lmerTest")`)


```{r T0 model selection, include=FALSE}

### Planning to model all measured values in response to parameter and species

## subsetting for T0 only
df_T0 <- subset(df2, T0_T90=="T0") # subset the dataframe for only T0 samples
df_T0 <- completeFun(df_T0, "value") # run function to remove any missing values


## running forloop to model each T0 CI per species in each parameter
param_list <- levels(factor(df_T0$param)) # create a list of parameter names

for (p in 1:length(param_list)) {
  
  # subset T0 dataframe by selected param name
  param_name <- param_list[p]
  T0_df_sub <- subset(df_T0, param == param_name)
  
  # run linear model 
  model <- lm(value ~ species, data = T0_df_sub) 
  out <- simulate(model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model response 2000 (bootnum)   times
  boots <- apply(out, 2, function(x) predict(lm(x ~ species, data = T0_df_sub), re.form=NA)) #   applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
  boots <- cbind(predict(model, re.form = NA), boots) # adds column to above df of predicted values without   random effects
  df_T0_a <- (cbind(T0_df_sub, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) #   apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual   values dataframe
  colnames(df_T0_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values
  
  ## save model results
  T0_df <- paste("LMER_model_outputs/T0_models/T0_model", param_name, date, sep="_") 
  T0_df <- paste(T0_df, ".csv", sep="") 
  write.csv(df_T0_a, file = T0_df)  # last saved model was: 2020-11-11
  
}



## read in all T0 model files and merge into single file
files <- fs::dir_ls(glob = "*csv", path = "LMER_model_outputs/T0_models/")
mergedT0 <- vroom(files)
write.csv(mergedT0, file = paste("LMER_model_outputs/T0_combined_out_", date, ".csv", sep=""))  # last saved model was: 2020-11-11

```


### Protein 

```{r protein model selection, include=FALSE}

## subsetting for protein only
df_pro <- subset(df2_T90, param=="pro") # subset the dataframe for only protein values
df_pro <- completeFun(df_pro, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
pro_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony), data = df_pro) # full model
pro_step <- step(pro_full_model) # run removal for best-fit model
pro_mod <- get_model(pro_step) # pull the final model
pro_mod_bestfit <- pro_mod@call[["formula"]] # pulls the model output
pro_mod_bestfit <- paste(format(pro_mod_bestfit))
anova(pro_mod) # run anova on best fit model 

```

While *`r pro_mod_bestfit`* was the best-fit model structure identified, we wanted to model both *p*CO~2~ and temperature responses by species so moving forward we are using the following model structure: 

**value ~ species * (fpco2 + ftemp) + (1 | colony)**


```{r protein bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_pro <- subset(df2_T90, param=="pro") # subset the dataframe for only protein values
df_pro <- completeFun(df_pro, "value") # run function to remove any missing protein values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML = TRUE, data = df_pro)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model protein response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML = TRUE, data = df_pro), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted protein values without random effects
df_pro_a <- (cbind(df_pro, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_pro_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

pro_df <- paste("LMER_model_outputs/Protein_model", date, sep="_") 
pro_df <- paste(pro_df, ".csv", sep="") 
write.csv(df_pro_a, file = pro_df)  # last saved model was: 2020-11-12

```

<br/>
Figure:

```{r protein figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_pro <- subset(df_T0_all, param == "pro")

## load the protein bootstrapped model output
df_pro_a <- read.csv("LMER_model_outputs/Protein_model_2020-11-12.csv", head = TRUE)
df_pro_a$ftemp <- as.factor(df_pro_a$ftemp)
df_pro_a$fpco2 <- as.factor(df_pro_a$fpco2)
df_pro_a$species <- factor(df_pro_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
pro_model_fig <- ggplot(df_pro_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8) +
  ylab(plab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_pro) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_pro)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/Protein_boot_figure_", date, ".pdf"), width = 10, height = 3)
pro_model_fig

```


### Carbohydrate 

```{r carbohydrate model selection, include=FALSE}

## subsetting for carbohydrate only
df_carb <- subset(df2_T90, param=="carb") # subset the dataframe for only carbohydrate values
df_carb <- completeFun(df_carb, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
carb_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony) + (1 | reef), data = df_carb) # full model
carb_step <- step(carb_full_model) # run removal for best-fit model
carb_mod <- get_model(carb_step) # pull the final model
carb_mod_bestfit <- carb_mod[["call"]][["formula"]] # pulls the model output
carb_mod_bestfit <- paste(format(carb_mod_bestfit))
carb_mod_bestfit <- paste0(carb_mod_bestfit[1])
anova(carb_mod) # run anova on best fit model 

```

While *`r carb_mod_bestfit`* was the best-fit model structure identified, we wanted to model responses with a random effect of colony so moving forward we are using the following model structure: 

**value ~ species * (fpco2 + ftemp) + (1 | colony)**


```{r carbohydrate bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_carb <- subset(df2_T90, param=="carb") # subset the T90 dataframe for only carbohydrate values
df_carb <- completeFun(df_carb, "value") # run function to remove any missing carbohydrate values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species * (fpco2 + ftemp) + (1 | colony), REML = TRUE, data = df_carb)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model carbohydrate response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + (1 | colony), REML = TRUE, data = df_carb), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted carbohydrate values without random effects
df_carb_a <- (cbind(df_carb, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_carb_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

carb_df <- paste("LMER_model_outputs/Carbohydrate_model", date, sep="_") 
carb_df <- paste(carb_df, ".csv", sep="") 
write.csv(df_carb_a, file = carb_df)  # last saved model was: 020-11-12

```

<br/>
Figure:

```{r carbohydrate figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_carb <- subset(df_T0_all, param == "carb")

## load the carbohydrate bootstrapped model output
df_carb_a <- read.csv("LMER_model_outputs/Carbohydrate_model_2020-11-12.csv", head=T)
df_carb_a$ftemp <- as.factor(df_carb_a$ftemp)
df_carb_a$fpco2 <- as.factor(df_carb_a$fpco2)
df_carb_a$species <- factor(df_carb_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
carb_model_fig <- ggplot(df_carb_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8)+
  ylab(calab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_carb) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_carb)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/Carbohydrate_boot_figure_", date, ".pdf"), width = 10, height = 3)
carb_model_fig

```


### Lipid 

```{r lipid model selection, include=FALSE}

## subsetting for lipid only
df_lipid <- subset(df2_T90, param=="lipid") # subset the dataframe for only lipid values
df_lipid <- completeFun(df_lipid, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
lipid_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony) + (1 | reef), data = df_lipid) # full model
lipid_step <- step(lipid_full_model) # run removal for best-fit model
lipid_mod <- get_model(lipid_step) # pull the final model
lipid_mod_bestfit <- lipid_mod[["call"]][["formula"]] # pulls the model output 
lipid_mod_bestfit <- paste(format(lipid_mod_bestfit))
anova(lipid_mod) # run anova on best fit model 

```

While *`r lipid_mod_bestfit`* was the best-fit model structure identified, we wanted to model both *p*CO~2~ and temperature responses by species and with random effect of colony so moving forward we are using the following model structure: 

**value ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony)**

```{r lipid bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_lipid <- subset(df2_T90, param=="lipid") # subset the T90 dataframe for only lipid values
df_lipid <- completeFun(df_lipid, "value") # run function to remove any missing lipid values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony), REML = TRUE, data = df_lipid)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model lipid response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony), REML = TRUE, data = df_lipid), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted lipid values without random effects
df_lipid_a <- (cbind(df_lipid, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_lipid_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

lipid_df <- paste("LMER_model_outputs/Lipid_model", date, sep="_") 
lipid_df <- paste(lipid_df, ".csv", sep="") 
write.csv(df_lipid_a, file = lipid_df)  # last saved model was: 2020-11-12

```

<br/>
Figure:

```{r lipid figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_lipid <- subset(df_T0_all, param == "lipid")

## load the lipid bootstrapped model output
df_lipid_a <- read.csv("LMER_model_outputs/Lipid_model_2020-11-12.csv", head=T)
df_lipid_a$ftemp <- as.factor(df_lipid_a$ftemp)
df_lipid_a$fpco2 <- as.factor(df_lipid_a$fpco2)
df_lipid_a$species <- factor(df_lipid_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
lipid_model_fig <- ggplot(df_lipid_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8)+
  ylab(llab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_lipid) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_lipid)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/Lipid_boot_figure_", date, ".pdf"), width = 10, height = 3)
lipid_model_fig

```


### Density 

```{r density model selection, include=FALSE}

## subsetting for density only
df_den <- subset(df2_T90, param=="den") # subset the dataframe for only density values
df_den <- completeFun(df_den, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
den_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony) + (1 | reef), data = df_den) # full model
den_step <- step(den_full_model) # run removal for best-fit model
den_mod <- get_model(den_step) # pull the final model
den_mod_bestfit <- den_mod@call[["formula"]] # pulls the model output
den_mod_bestfit <- paste(format(den_mod_bestfit))
den_mod_bestfit <- paste0(den_mod_bestfit[1], den_mod_bestfit[2], den_mod_bestfit[3], den_mod_bestfit[4])
anova(den_mod) # run anova on best fit model 

```

While *`r den_mod_bestfit`* was the best-fit model structure identified, we wanted to model both *p*CO~2~ and temperature responses by species and with random effect of colony so moving forward we are using the following model structure: 

**value ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony)**


```{r density bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_den <- subset(df2_T90, param=="den") # subset the T90 dataframe for only density values
df_den <- completeFun(df_den, "value") # run function to remove any missing density values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony), REML = TRUE, data = df_den)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model density response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species * (fpco2 + ftemp) + reef + species:reef + (1 | colony), REML = TRUE, data = df_den), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted density values without random effects
df_den_a <- (cbind(df_den, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_den_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

den_df <- paste("LMER_model_outputs/Density_model", date, sep="_") 
den_df <- paste(den_df, ".csv", sep="") 
write.csv(df_den_a, file = den_df)  # last saved model was: Density_model_2020-11-05.csv

```

<br/>
Figure:

```{r density figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_den <- subset(df_T0_all, param == "den")

## load the density bootstrapped model output
df_den_a <- read.csv("LMER_model_outputs/Density_model_2020-11-12.csv", head=T)
df_den_a$ftemp <- as.factor(df_den_a$ftemp)
df_den_a$fpco2 <- as.factor(df_den_a$fpco2)
df_den_a$species <- factor(df_den_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
den_model_fig <- ggplot(df_den_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8)+
  ylab(dlab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_den) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_den)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/Density_boot_figure_", date, ".pdf"), width = 10, height = 3)
den_model_fig

```


### Chlorophyll 

```{r chlorophyll model selection, include=FALSE}

## subsetting for chlorophyll only
df_chla <- subset(df2_T90, param=="chla") # subset the dataframe for only chlorophyll values
df_chla <- completeFun(df_chla, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
chla_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony) + (1 | reef), data = df_chla) # full model
chla_step <- step(chla_full_model) # run removal for best-fit model
chla_mod <- get_model(chla_step) # pull the final model
chla_mod_bestfit <- chla_mod@call[["formula"]] # pulls the model output
chla_mod_bestfit <- paste(format(chla_mod_bestfit))
chla_mod_bestfit <- paste0(chla_mod_bestfit[1], chla_mod_bestfit[2])
anova(chla_mod) # run anova on best fit model 

```

Since the best-fit model fits our design, we will proceed with the following model structure: 

**`r chla_mod_bestfit`**

```{r chlorophyll bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_chla <- subset(df2_T90, param=="chla") # subset the T90 dataframe for only chlorophyll values
df_chla <- completeFun(df_chla, "value") # run function to remove any missing chlorophyll values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species + fpco2 + ftemp + reef + species:fpco2 + species:ftemp + fpco2:ftemp + species:reef + (1 | colony), REML = TRUE, data = df_chla)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model chlorophyll response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species + fpco2 + ftemp + reef + species:fpco2 + species:ftemp + fpco2:ftemp + species:reef + (1 | colony), REML = TRUE, data = df_chla), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted chlorophyll values without random effects
df_chla_a <- (cbind(df_chla, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_chla_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

chla_df <- paste("LMER_model_outputs/Chlorophyll_model", date, sep="_") 
chla_df <- paste(chla_df, ".csv", sep="") 
write.csv(df_chla_a, file = chla_df)  # last saved model was: Chlorophyll_model_2020-11-05.csv

```

<br/>
Figure:

```{r chlorophyll figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_chla <- subset(df_T0_all, param == "chla")

## load the chlorophyll bootstrapped model output
df_chla_a <- read.csv("LMER_model_outputs/Chlorophyll_model_2020-11-12.csv", head=T)
df_chla_a$ftemp <- as.factor(df_chla_a$ftemp)
df_chla_a$fpco2 <- as.factor(df_chla_a$fpco2)
df_chla_a$species <- factor(df_chla_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
chla_model_fig <- ggplot(df_chla_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8)+
  ylab(clab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_chla) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_chla)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/Chlorophyll_boot_figure_", date, ".pdf"), width = 10, height = 3)
chla_model_fig

```


### Total Host 

```{r total host model selection, include=FALSE}

## subsetting for total host only
df_host <- subset(df2_T90, param=="host") # subset the dataframe for only total host values
df_host <- completeFun(df_host, "value") # run function to remove any missing values

## run the full mixed-effects model for backwards removal of non-significant effects (using lmerTest version 3.1-3)
host_full_model <- lmer(value ~ species * fpco2 * ftemp * reef + (1 | colony) + (1 | reef), data = df_host) # full model
host_step <- step(host_full_model) # run removal for best-fit model
host_mod <- get_model(host_step) # pull the final model
host_mod_bestfit <- host_mod@call[["formula"]] # pulls the model output 
host_mod_bestfit <- paste(format(host_mod_bestfit))
host_mod_bestfit <- paste0(host_mod_bestfit[1], host_mod_bestfit[2])
anova(host_mod) # run anova on best fit model 

```

Since the best-fit model fits our design, we will proceed with the following model structure: 

**`r host_mod_bestfit`**

```{r total host bootstrapping, eval=FALSE}

## subsetting (if you did not already do this in running the AIC selection script)
df_host <- subset(df2_T90, param=="host") # subset the T90 dataframe for only total host values
df_host <- completeFun(df_host, "value") # run function to remove any missing total host values

## mixed effect model run using lmer() (lmerTest version 3.1-3)
T90_df_model <- lmer(value ~ species + fpco2 + ftemp + reef + species:fpco2 + species:ftemp + species:reef + fpco2:reef + species:fpco2:reef + (1 | colony), REML = TRUE, data = df_host)
out <- simulate(T90_df_model, nsim = bootnum, seed = seed, re.form = NULL) # simulate model total host response 2000 (bootnum) times (using random effects)
boots <- apply(out, 2, function(x) predict(lmer(x ~ species + fpco2 + ftemp + reef + species:fpco2 + species:ftemp + species:reef + fpco2:reef + species:fpco2:reef + (1 | colony), REML = TRUE, data = df_host), re.form=NA)) # applies predict function on the columns (2) of the 'out' matrix created above from simulating the model 
boots <- cbind(predict(T90_df_model, re.form = NA), boots) # adds column to above df of predicted total host values without random effects
df_host_a <- (cbind(df_host, as.data.frame(t(apply(boots, 1, function(x) c(mean(x), quantile(x, c(0.025, 0.975)))))))) # apply function to calculate mean and 95% CI per sample based on the bootstrapped values, then add these to the actual values dataframe
colnames(df_host_a)[17:19] <- c("mean", "lowerci", "upperci") # rename columns with bootstrapped values

host_df <- paste("LMER_model_outputs/TotalHost_model", date, sep="_") 
host_df <- paste(host_df, ".csv", sep="") 
write.csv(df_host_a, file = host_df)  # last saved model was: TotalHost_model_2020-11-05.csv

```

<br/>
Figure:

```{r total host figure, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

## need to add T0 samples to the plot (but these are modeled in different bootstrapping)
df_T0_all <- read.csv("LMER_model_outputs/T0_combined_out_2020-11-12.csv", header = TRUE)
df_T0_host <- subset(df_T0_all, param == "host")

## load the host bootstrapped model output
df_host_a <- read.csv("LMER_model_outputs/TotalHost_model_2020-11-12.csv", head=T)
df_host_a$ftemp <- as.factor(df_host_a$ftemp)
df_host_a$fpco2 <- as.factor(df_host_a$fpco2)
df_host_a$species <- factor(df_host_a$species, levels = c("SSID", "PSTR", "PAST", "UTEN"))

## plot figure
host_model_fig <- ggplot(df_host_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", size= 0.8))+
  scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  geom_vline(xintercept = 3, size= 0.8)+
  ylab(hlab)+
  xlab("")+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_point(aes(x = treat, y = value, colour = ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2, data = df_T0_host) + # add T0 samples
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  geom_linerange(aes(x = treat, ymin = lowerci, ymax = upperci), colour = "#009E73", position = dodge, size = 1, data = df_T0_host)+ # add T0 CIs
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 3, scales = "free_y") +
  ggsave(paste0("Figures/TotalHost_boot_figure_", date, ".pdf"), width = 10, height = 3)
host_model_fig

```





### Calcification

*This is the same model from Bove et al 2019, just matching aesthetics for this manuscript.*

```{r calcification rate, fig.height = 2, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

ncalc_a<-read.csv("net_calc.csv")
#ncalc_a <- subset(ncalc_a, species != "T")
ncalc_a$ftemp <- as.factor(ncalc_a$ftemp)
ncalc_a$fpco2 <- as.factor(ncalc_a$fpco2)
ncalc_a <- subset(ncalc_a, species != "T")
ncalc_a$species <- factor(ncalc_a$species, levels = c("S", "P", "A"))

calc_model_fig <- ggplot(ncalc_a)+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="none", panel.border = element_rect(colour = "black", fill=NA, size=1))+
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  #scale_x_continuous(breaks = ncalc_a$treat, labels = ncalc_a$fpco2)+
  ylab(rlab)+
  xlab("")+
  geom_point(aes(x = fpco2, y = rate, colour=ftemp), position = dodge2, alpha = 0.3, shape = 17, size = 2)+
  geom_linerange(aes(x = fpco2, ymin = lowerci, ymax = upperci, colour = ftemp), position = dodge, size = 1)+
  scale_color_manual("Temperature", values = c("#0072B2", "#D55E00", "#009E73"))+
  facet_wrap(~species, ncol = 4, scales = "free_y")

calc_model_fig

```


### **Figure 1** 

```{r figure 3, fig.height = 10, fig.width = 10, fig.align = "center", results = 'hide', message=FALSE}

fig1 <- plot_grid(corals, host_model_fig, den_model_fig, chla_model_fig, labels = c("A", "B", "C", "D"), ncol = 1, align = "v", axis = 'lb')
fig1

ggsave("Fig1_physiology_18Dec19.pdf")

```
<br/>
**Figure 1.** Modeled 95% confidence interval of (**A**) total host energy reserves (mg cm^-2^), (**B**) cell density (10^6^ cells cm^-2^), and (**C**) Chlorophyll a (ug cm^-2^) for *S. siderea*, *P. strigosa*, and *P. astreoides* at T0 (green) or T90 (<span style="color: #D55E00;">red</span>/<span style="color: #0072B2;">blue</span>), with individual coral fragment physiology denoted by points. <span style="color: #0072B2;">Blue</span> denotes 28&deg;C and <span style="color: #D55E00;">red</span> denotes 31&deg;C, with *p*CO~2~ treatment along the x axis.

<br/>


## Correlation assessments{.tabset}

Here, I am exploring the relationships between each physiology parameter measured above.

```{r T90 df setup}

df_90 <- subset(df, T0_T90 == "T90") 
df_90 <- subset(df_90, species != "T") 
df_90 <- df_90[,-c(18:33)]
df_90 <- completeFun(df_90, "den")
df_90 <- completeFun(df_90, "host")
df_90 <- completeFun(df_90, "lipid")
df_90 <- completeFun(df_90, "carb")
df_90_l <- gather(df_90, param, value, 14:23)

## specific species dataframes
s_df <- subset(df_90, species == "S") 
p_df <- subset(df_90, species == "P") 
a_df <- subset(df_90, species == "A") 

```

```{r correlation df setup}

## dataframe updates
df_90$ID <- paste(df_90$coral, df_90$treat2, sep = "_") # add coral name to treatment

df_subset <- as.data.frame(df_90[,c(26,8,14:18,21:23)]) # subset the df for desired columns
df_subset <- df_subset[!duplicated(df_subset$ID), ] # remove any duplicated values
rownames(df_subset) <- df_subset$ID # rename rows with ID

# create dataframes for each species
sid_df <- subset(df_subset, species == "S")
dip_df <- subset(df_subset, species == "P")
por_df <- subset(df_subset, species == "A")


## create matrix for correlations by species
sid_corr_df2 <- rcorr(as.matrix(sid_df[, c(4,9,10,3,5,6,8)])) # from these correlations, going to stick with red channel for corr/PCA input
#sid_corr_df2 # correlation matrix
#sid_corr_df2$r # R2 of all correlations
#sid_corr_df2$P # p value of all correlations
sid_corr_df2$r[sid_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

dip_corr_df2 <- rcorr(as.matrix(dip_df[, c(4,9,10,3,5,6,8)])) # from these correlations, going to stick with red channel for corr/PCA input
#dip_corr_df2 # correlation matrix
#dip_corr_df2$r # R2 of all correlations
#dip_corr_df2$P # p value of all correlations
dip_corr_df2$r[dip_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

por_corr_df2 <- rcorr(as.matrix(por_df[, c(4,9,10,3,5,7,8)])) # from these correlations, going to stick with sum of channels for corr/PCA input
#por_corr_df2 # correlation matrix
#por_corr_df2$r # R2 of all correlations
#por_corr_df2$P # p value of all correlations
por_corr_df2$r[por_corr_df2$r < 0] <- 0 # this just makes negative correlations 0 since none are significant (easier for plotting)

```

```{r correlation matrix plot method 1, eval=FALSE, include=FALSE}

### This is the first method of a correlation plot. It was not used, but kept in for records.

## Insignificant correlation are left out
# SSID
corrplot(sid_corr_df2$r, type="upper", order="hclust", p.mat = sid_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
sid_corr_plot <- grid.grab()

# PSTR
corrplot(dip_corr_df2$r, type="upper", order="hclust", p.mat = dip_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
dip_corr_plot <- grid.grab()

# PAST
corrplot(por_corr_df2$r, type="upper", order="hclust", p.mat = por_corr_df2$P, sig.level = 0.05, insig = "p-value", method = "ellipse", tl.col = "black")
grid.echo()
por_corr_plot <- grid.grab()

#grid.draw(P1)

plot_grid(sid_corr_plot, dip_corr_plot, por_corr_plot, ncol = 1, labels = "AUTO")

```

```{r actual correlation matrix plot}

## Final correlation plot (and saving it as PDF)
# Rmarkdown plotting version
par(mfrow=c(2,2))
corrplot.mixed(sid_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = sid_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("S. siderea")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(dip_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = dip_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("P. strigosa")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(por_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = por_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("P. asteroides")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

```

<br/>
**Figure 2.** Correlation matrix for *S. siderea*, *P. strigosa*, and *P. astreoides* depicting pair-wise comparisons of physiological parameters within each species. Colour and ellipse width denote R^2^ of each significant comparison, and blank grids represent non-significant pair-wise comparisons (*P* > 0.05).Each parameter is denoted in <span style="color: #0072B2;">blue</span> text along the diagonal of each plot. Correlations with R^2^ above 0.5 (shown in <span style="color: #E67D00;">orange</span> and <span style="color: #F21A00;">red</span> in matrix plot) are explored further below.

<br/>

```{r save correlation plot, message=FALSE, warning=FALSE, include=FALSE}

# below saves the figure
pdf(file = "Figures/CorrelationPlot.pdf", width = 10, height = 8)  

par(mfrow=c(2,2))
corrplot.mixed(sid_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = sid_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("S. siderea")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(dip_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = dip_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("P. strigosa")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

corrplot.mixed(por_corr_df2$r, upper = "ellipse", lower.col = "darkslategrey", upper.col = wes_palette("Zissou1", 7, type = "continuous"), number.cex = 0.8, p.mat = por_corr_df2$P, sig.level = c(.001, .01, .05), insig = "blank", tl.col = "#0072B2", tl.cex = 1.1, title = expression(italic("P. asteroides")), cl.lim = c(0,1), mar=c(0,0,1,0), cl.align.text = "l")

dev.off() 

par(mfrow = c(1, 1))

```


### *Siderastrea siderea*

```{r SSID scatter plots, fig.width = 7, fig.height = 12}

#s_df <- subset(s_df, T0_T90 == "T90")
 
sid_denVrate <- ggplot(data = s_df, aes(x = den, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(dlab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

sid_chlaVrate <- ggplot(data = s_df, aes(x = chla, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(clab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_sumVrate <- ggplot(data = s_df, aes(x = sum, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(rlab) + 
  xlab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_denVsum <- ggplot(data = s_df, aes(x = sum, y = den, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(dlab) + 
  xlab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_denVchla <- ggplot(data = s_df, aes(x = chla, y = den, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(dlab) + 
  xlab(clab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_denVpro <- ggplot(data = s_df, aes(x = pro, y = den, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(dlab) + 
  xlab(plab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_chlaVpro <- ggplot(data = s_df, aes(x = pro, y = chla, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(clab) + 
  xlab(plab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

sid_carbVpro <- ggplot(data = s_df, aes(x = pro, y = carb, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(calab) + 
  xlab(plab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()



plot_grid(sid_denVrate, sid_chlaVrate, sid_sumVrate, sid_denVsum, sid_denVchla, sid_denVpro, sid_chlaVpro, sid_carbVpro, labels = "AUTO", ncol = 2, scale = 0.9)

#ggsave("Ch3_appFig_SSIDscatter_29Jan20.pdf", width = 10, height = 14, units = "in")

```

<br/>

### *Pseudodiploria strigosa*

```{r PSTR scatter plots, fig.width = 6, fig.height = 20}

#p_df <- subset(p_df, T0_T90 == "T90")

dip_proVlipid <- ggplot(data = s_df, aes(x = pro, y = lipid, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab(llab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_proVcarb <- ggplot(data = s_df, aes(x = pro, y = carb, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab(calab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_proVden <- ggplot(data = s_df, aes(x = pro, y = den, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab(dlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_proVchla <- ggplot(data = s_df, aes(x = pro, y = chla, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab(clab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_proVsum <- ggplot(data = s_df, aes(x = pro, y = sum, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_proVrate <- ggplot(data = s_df, aes(x = pro, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(plab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_carbVlipid <- ggplot(data = s_df, aes(x = carb, y = lipid, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(calab) + 
  ylab(llab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_carbVden <- ggplot(data = s_df, aes(x = carb, y = den, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(calab) + 
  ylab(dlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_carbVchla <- ggplot(data = s_df, aes(x = carb, y = chla, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(calab) + 
  ylab(clab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_carbVsum <- ggplot(data = s_df, aes(x = carb, y = sum, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(calab) + 
  ylab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_carbVrate <- ggplot(data = s_df, aes(x = carb, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(calab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_denVchla <- ggplot(data = s_df, aes(x = den, y = chla, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(dlab) + 
  ylab(clab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_denVsum <- ggplot(data = s_df, aes(x = den, y = sum, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(dlab) + 
  ylab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_denVrate <- ggplot(data = s_df, aes(x = den, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(dlab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_chlaVsum <- ggplot(data = s_df, aes(x = chla, y = sum, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(dlab) + 
  ylab("Sum colour intensity") +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_chlaVrate <- ggplot(data = s_df, aes(x = chla, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(clab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()

dip_sumVrate <- ggplot(data = s_df, aes(x = sum, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab("Sum colour intensity") + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 3.9) +
  #stat_regline_equation(label.y = -0.7, label.x = 3.9) +
  geom_point()


plot_grid(dip_proVcarb, dip_proVlipid, dip_proVden, dip_proVchla, dip_proVsum, dip_proVrate, dip_carbVlipid, dip_carbVden, dip_carbVchla, dip_carbVsum, dip_carbVrate, dip_denVchla, dip_denVsum, dip_denVrate, dip_chlaVsum, dip_chlaVrate, dip_sumVrate, labels = "AUTO", ncol = 2, scale = 0.9)


#ggsave("Ch3_appFig_PSTRscatter_29Jan20.pdf", width = 10, height = 14, units = "in")

```

<br/>

### *Porites astreoides* 

```{r PAST scatter plots, fig.width = 7, fig.height = 9}

#a_df <- subset(a_df, T0_T90 == "T90")

por_chlaVrate <- ggplot(data = s_df, aes(x = chla, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  xlab(clab) + 
  ylab(rlab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #geom_smooth(method = "lm", aes(group = fpco2), se = FALSE) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

por_redVchla <- ggplot(data = s_df, aes(x = chla, y = red, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab("Red colour intensity") + 
  xlab(clab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

por_rateVpro <- ggplot(data = s_df, aes(x = pro, y = rate, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(rlab) + 
  xlab(plab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

por_carbVlipid <- ggplot(data = s_df, aes(x = carb, y = lipid, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(calab) + 
  xlab(llab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()

por_carbVpro <- ggplot(data = s_df, aes(x = pro, y = carb, colour = fpco2, shape = ftemp, group = species)) +
  theme_classic() +
  theme(legend.position = "none") +
  ylab(calab) + 
  xlab(plab) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101")) +
  scale_shape_manual("temperature", labels = c("28C", "31C"), values = c(19,1)) +
  #stat_cor(label.y = -0.5, label.x = 150) +
  #stat_regline_equation(label.y = -0.7, label.x = 150) +
  geom_point()



plot_grid(por_chlaVrate, por_redVchla, por_rateVpro, por_carbVlipid, por_carbVpro, labels = "AUTO", ncol = 2, scale = 0.9)

#ggsave("Ch3_appFig_PASTscatter_29Jan20.pdf", width = 10, height = 14, units = "in")

```


<br/>

## Holobiont PCAs{.tabset} 

### *Siderastrea siderea*

```{r SSID PCA}

# set up the dataframe
s_df_l <- gather(s_df, param, value, c(14:16,21:23))
s_df$fpco2 <- factor(s_df$fpco2, levels = c("300", "420", "680", "3300"))

# run the adonis
#s_pca_mod <- adonis(value ~ reef * ftemp * fpco2, data = s_df_l, method='eu') # below is the model with non sig interactions removed:
s_pca_mod <- adonis(value ~ reef + ftemp + fpco2, data = s_df_l, method='eu')
s_pca_mod # view SSID adonis output

# extract pvalues
s_pval <- s_pca_mod[["aov.tab"]][["Pr(>F)"]]

# perform principal component analysis (PCA)
s_pca <- prcomp(s_df[,c(14:16,21:23)], center = TRUE, scale= TRUE)

```

```{r SSID PCA plot, fig.height=8, fig.width=8}

# create labels for p values calculated above
s_reef_pval <-substitute(italic(P[reef])==p, list(p = format(s_pval[1], digits = 2)))
s_temp_pval <-substitute(italic(P[temp])==p, list(p = format(s_pval[2], digits = 3)))
s_pco2_pval <-substitute(italic(P[pCO[2]])==p, list(p = format(s_pval[3], digits = 2)))

# reef environment
s_reef_pca <- autoplot(s_pca, data = s_df, 
         colour = "reef",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 3, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b")) +
  scale_fill_manual("reef environment", labels = c("offshore", "inshore"), values = c(NA, NA)) +  
  lims(x = c(-0.5,0.4), y = c(-0.4,0.4)) +
  guides(col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top")) +  
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none") +
  annotate("text", x = -0.39, y = -0.38, label = deparse(s_reef_pval), parse = TRUE, size = 3) +
  ggtitle("Reef Environment")

# temperature
s_temp_pca <- autoplot(s_pca, data = s_df, 
         colour = "ftemp",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 3, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  scale_fill_manual("temperature", labels = c("28C", "31C"), values = c(NA, NA))+
  lims(x = c(-0.5,0.4), y = c(-0.4,0.4)) +
  scale_shape_manual("pCO2", labels = c("pre industrial", "pre industrial", "current", "current", "end-of-century","end-of-century", "extreme", "extreme"), values = c(0,15,1,16,2,17,5,18))+
  guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+  
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none") +
  annotate("text", x = -0.34, y = -0.38, label = deparse(s_temp_pval), parse = TRUE, size = 3) +  
  ggtitle("Temperature")

# pco2
s_pco2_pca <- autoplot(s_pca, data = s_df, 
         colour = "fpco2",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = 3, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
    scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101"))+
    scale_fill_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c(NA, NA, NA, NA))+
    lims(x = c(-0.5,0.4), y = c(-0.4,0.4)) +   
    scale_shape_manual("temperature", labels = c("28C", "31C", "28C", "31C", "28C", "31C", "28C", "31C"), values = c(0,15,1,16,2,17,5,18))+
    guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none") +
  annotate("text", x = -0.365, y = -0.38, label = deparse(s_pco2_pval), parse = TRUE, size = 3) +   
  ggtitle("Acidification")


plot_grid(s_temp_pca, s_pco2_pca, s_reef_pca, ncol = 2, scale = 0.8) # markdown figure

SSID_plot <- plot_grid(s_temp_pca, s_pco2_pca, s_reef_pca, ncol = 3, scale = 0.8) # for final figure

```

### *Pseudodiploria strigosa*

```{r PSTR PCA}

# set up the dataframe
p_df_l <- gather(p_df, param, value, c(14:16,21:23))
p_df$fpco2 <- factor(p_df$fpco2, levels = c("300", "420", "680", "3300"))

# run the adonis
#p_pca_mod <- adonis(value ~ reef * ftemp * fpco2, data = p_df_l, method='eu') # below is the model with non sig interactions removed:
p_pca_mod <- adonis(value ~ reef + ftemp + fpco2, data = p_df_l, method='eu')
p_pca_mod # view PSTR adonis output

# extract pvalues
p_pval <- p_pca_mod[["aov.tab"]][["Pr(>F)"]]

# perform principal component analysis (PCA)
p_pca <- prcomp(p_df[,c(14:16,21:23)], center = TRUE, scale= TRUE)

```

```{r PSTR PCA plot, fig.height=8, fig.width=8}

# create labels for p values calculated above
p_reef_pval <-substitute(italic(P[reef])==p, list(p = format(p_pval[1], digits = 2)))
p_temp_pval <-substitute(italic(P[temp])==p, list(p = format(p_pval[2], digits = 3)))
p_pco2_pval <-substitute(italic(P[pCO[2]])==p, list(p = format(p_pval[3], digits = 2)))

# reef environment
p_reef_pca <- autoplot(p_pca, data = p_df, 
         colour = "reef",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 2,
         loadings.label.repel = TRUE) +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b"))+
  scale_fill_manual("reef environment", labels = c("offshore", "inshore"), values = c(NA, NA))+
  guides(col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top")) +  
  lims(x = c(-0.5,0.5), y = c(-0.5,0.7)) +   
  annotate("text", x = -0.36, y = -0.48, label = deparse(p_reef_pval), parse = TRUE, size = 3) +     
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none")

# temperature
p_temp_pca <- autoplot(p_pca, data = p_df, 
         colour = "ftemp",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 2,
         loadings.label.repel = TRUE) +
  scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  scale_fill_manual("temperature", labels = c("28C", "31C"), values = c(NA, NA))+
  scale_shape_manual("pCO2", labels = c("pre industrial", "pre industrial", "current", "current", "end-of-century","end-of-century", "extreme", "extreme"), values = c(0,15,1,16,2,17,5,18))+
  guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+ 
  lims(x = c(-0.5,0.5), y = c(-0.5,0.7)) +   
  annotate("text", x = -0.345, y = -0.48, label = deparse(p_temp_pval), parse = TRUE, size = 3) + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none")

# pco2
p_pco2_pca <- autoplot(p_pca, data = p_df, 
         colour = "fpco2",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 2,
         loadings.label.repel = TRUE) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101"))+
  scale_fill_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c(NA, NA, NA, NA))+
  scale_shape_manual("temperature", labels = c("28C", "31C", "28C", "31C", "28C", "31C", "28C", "31C"), values = c(0,15,1,16,2,17,5,18))+
  guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+
  lims(x = c(-0.5,0.5), y = c(-0.5,0.7)) +   
  annotate("text", x = -0.345, y = -0.48, label = deparse(p_pco2_pval), parse = TRUE, size = 3) + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "none")

plot_grid(p_temp_pca, p_pco2_pca, p_reef_pca, ncol = 2, scale = 0.8) # markdown figure

PSTR_plot <- plot_grid(p_temp_pca, p_pco2_pca, p_reef_pca, ncol = 3, scale = 0.8) # for plotting final figure

```

### *Porites astreoides*

```{r PAST PCA}

# set up the dataframe
a_df_l <- gather(a_df, param, value, c(14:16,21:23))
a_df$fpco2 <- factor(a_df$fpco2, levels = c("300", "420", "680", "3300"))

# run the adonis
#a_pca_mod <- adonis(value ~ reef * ftemp * fpco2, data = a_df_l, method='eu') # below is the model with non sig interactions removed:
a_pca_mod <- adonis(value ~ reef + ftemp + fpco2, data = a_df_l, method='eu')
a_pca_mod # view PAST adonis output

# extract pvalues
a_pval <- a_pca_mod[["aov.tab"]][["Pr(>F)"]]

# perform principal component analysis (PCA)
a_pca <- prcomp(a_df[,c(14:16,21:23)], center = TRUE, scale= TRUE)

```

```{r PAST PCA plot, fig.height=8, fig.width=8}

# create labels for p values calculated above
a_reef_pval <-substitute(italic(P[reef])==p, list(p = format(a_pval[1], digits = 2)))
a_temp_pval <-substitute(italic(P[temp])==p, list(p = format(a_pval[2], digits = 3)))
a_pco2_pval <-substitute(italic(P[pCO[2]])==p, list(p = format(a_pval[3], digits = 2)))

# reef environment
a_reef_pca <- autoplot(a_pca, data = a_df, 
         colour = "reef",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b"))+
  scale_fill_manual("reef environment", labels = c("offshore", "inshore"), values = c(NA, NA))+
  guides(col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+  
  lims(x = c(-0.5,0.4), y = c(-0.5,0.45)) +   
  annotate("text", x = -0.37, y = -0.49, label = deparse(a_reef_pval), parse = TRUE, size = 3) + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "bottom", legend.title = element_blank())

# temperature
a_tema_pca <- autoplot(a_pca, data = a_df, 
         colour = "ftemp",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("temperature", labels = c("28C", "31C"), values = c("#0072B2", "#D55E00"))+
  scale_fill_manual("temperature", labels = c("28C", "31C"), values = c(NA, NA))+
  scale_shape_manual("pCO2", labels = c("pre industrial", "pre industrial", "current", "current", "end-of-century","end-of-century", "extreme", "extreme"), values = c(0,15,1,16,2,17,5,18))+
  guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+  
  lims(x = c(-0.5,0.4), y = c(-0.5,0.45)) +   
  annotate("text", x = -0.36, y = -0.49, label = deparse(a_temp_pval), parse = TRUE, size = 3) + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "bottom", legend.title = element_blank())

# pco2
a_pco2_pca <- autoplot(a_pca, data = a_df, 
         colour = "fpco2",
         shape = "treat2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c("#b2abd2", "#5e3c99", "#fdb863", "#e66101"))+
  scale_fill_manual("pCO2", labels = c("pre industrial", "current", "end-of-century", "extreme"), values = c(NA, NA, NA, NA))+
  scale_shape_manual("temperature", labels = c("28C", "31C", "28C", "31C", "28C", "31C", "28C", "31C"), values = c(0,15,1,16,2,17,5,18))+
  guides(shape = FALSE, col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top"))+
  lims(x = c(-0.5,0.4), y = c(-0.5,0.45)) +   
  annotate("text", x = -0.35, y = -0.49, label = deparse(a_pco2_pval), parse = TRUE, size = 3) + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "bottom", legend.title = element_blank())

plot_grid(a_tema_pca, a_pco2_pca, a_reef_pca, ncol = 2, scale = 0.8) # markdown figure

PAST_plot <- plot_grid(a_tema_pca, a_pco2_pca, a_reef_pca, ncol = 3, scale = 0.8) # for plotting final figure

```

### **Figure 2**

```{r PCA plot, fig.height=12, fig.width=11}

plot_grid(SSID_plot, PSTR_plot, PAST_plot, ncol = 1, labels = c("A", "B", "C"), rel_heights = c(0.82, 0.75, 1)) +
  ggsave("Figure2_PhysPCA.pdf", width = 11.5, height = 12)

```


## Plasticity analyses{.tabset} 

### Control Comparison (400 $\mu$atm; 28 &deg;C)

#### *S. siderea*

aov(distance ~ *p*CO2 * temperature * reef)

```{r SSID distance dataframe setup}

s_dis <- s_pca$x[,1:2] # grab PC1 and PC2 distances from prcomp() object

sid_dist <- cbind(s_df[,c(1,7,10,11,12,9,25)], s_dis) # combine the datasets

sid_dist$cont_pc1[sid_dist$treat2 == "447_28"] <- sid_dist$PC1[sid_dist$treat2 == "447_28"] # this adds column with the control value PC1 per colony
sid_dist$cont_pc2[sid_dist$treat2 == "447_28"] <- sid_dist$PC2[sid_dist$treat2 == "447_28"] # this adds column with the control value PC2 per colony

# get the 400_28 PC values
sid_dist2 <- sid_dist %>%  
  group_by(colony) %>% 
  summarise(con2_pc1 = sum(cont_pc1, na.rm = TRUE))
sid_dist3 <- sid_dist %>% 
  group_by(colony) %>% 
  summarise(con2_pc2 = sum(cont_pc2, na.rm = TRUE))

# Make columns of the 400_28 PC values
sid_dist <- sid_dist %>% 
  left_join(sid_dist2, by = c("colony" = "colony"))
sid_dist <- sid_dist %>% 
  left_join(sid_dist3, by = c("colony" = "colony"))

sid_dist$dist <- sqrt(((sid_dist$PC1 - sid_dist$con2_pc1)^2) + ((sid_dist$PC2 - sid_dist$con2_pc2)^2)) # formula for calculating distance between control (T90) and treatment values
sid_dist$treat_plot <- paste(sid_dist$fpco2, sid_dist$ftemp, sep = "_")

```

```{r SSID distance analysis}

s_dis_aov <- aov(dist ~ fpco2 * ftemp * reef, data = sid_dist)
summary(s_dis_aov)
sid_dis_tuk <- TukeyHSD(s_dis_aov)

sid_dis_tab <- as.data.frame(sid_dis_tuk$`treat2:reef`)
sid_dis_tab$treat <- rownames(sid_dis_tab)

```

Reef environment:
```{r}

sid_dis_tuk$reef

```

Temperature:
```{r}

sid_dis_tuk$ftemp
```

*p*CO~2~:
```{r}

sid_dis_tuk$fpco2

```

<br/>

```{r plots of SSID distances, fig.height = 3, fig.width = 10}

# just treatment
sid_dist_sum2 <- summarySE(measurevar = "dist", groupvars = c("fpco2", "ftemp", "reef"), data = sid_dist)
sid_dist_sum2$treat <- paste(sid_dist_sum2$fpco2, sid_dist_sum2$ftemp, sep = "_")
sid_dist$treat_plot <- ordered(sid_dist$treat_plot, levels = c("300_28", "300_31", "420_28", "420_31", "680_28", "680_31", "3300_28", "3300_31"))

sid_con_dis_plot <- ggplot(sid_dist_sum2) +
  theme_bw() +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="right", panel.border = element_rect(colour = "black", size= 0.8)) +
  #scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  ylab("Mean distance from control") +
  xlab("") +
  ylim(0, 7) +
  #geom_point(aes(x = treat, y = dist, colour = reef), position = dodge, alpha = 0.3, shape = 17, size = 2) +
  geom_point(aes(x = treat_plot, y = dist, colour = reef), position = dodge, alpha = 0.3, size = 2.5, data = sid_dist) +
  geom_errorbar(position = dodge, aes(x = treat, ymin = dist - se, ymax = dist + se, colour = reef), width = 0, size = 1.5) +
  geom_vline(xintercept = c(2.5, 4.5, 6.5)) +
  annotate("text", x = 1, y = 7, label = "pre-industrial") +
  annotate("text", x = 3, y = 7, label = "present-day") +
  annotate("text", x = 5.1, y = 7, label = "end-of-century") +
  annotate("text", x = 6.9, y = 7, label = "extreme") +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b"))
sid_con_dis_plot

```

---

<br/>


#### *P. strigosa*

aov(distance ~ *p*CO2 + temperature + reef + *p*CO2:temperature)

```{r PSTR distance dataframe setup}

p_dis <- p_pca$x[,1:2] # grab PC1 and PC2 distances from prcomp() object

dip_dist <- cbind(p_df[,c(1,7,10,11,12,9,25)], p_dis) # combine the datasets

dip_dist$cont_pc1[dip_dist$treat2 == "447_28"] <- dip_dist$PC1[dip_dist$treat2 == "447_28"] # this adds column with the control value PC1 per colony
dip_dist$cont_pc2[dip_dist$treat2 == "447_28"] <- dip_dist$PC2[dip_dist$treat2 == "447_28"] # this adds column with the control value PC2 per colony

# get the 400_28 PC values
dip_dist2 <- dip_dist %>%  
  group_by(colony) %>% 
  summarise(con2_pc1 = sum(cont_pc1, na.rm = TRUE))
dip_dist3 <- dip_dist %>% 
  group_by(colony) %>% 
  summarise(con2_pc2 = sum(cont_pc2, na.rm = TRUE))

# Make columns of the 400_28 PC values
dip_dist <- dip_dist %>% 
  left_join(dip_dist2, by = c("colony" = "colony"))
dip_dist <- dip_dist %>% 
  left_join(dip_dist3, by = c("colony" = "colony"))

dip_dist$dist <- sqrt(((dip_dist$PC1 - dip_dist$con2_pc1)^2) + ((dip_dist$PC2 - dip_dist$con2_pc2)^2)) # formula for calculating distance between control (T90) and treatment values
dip_dist$treat_plot <- paste(dip_dist$fpco2, dip_dist$ftemp, sep = "_")

```

```{r PSTR distance analysis}

p_dip_aov <- aov(dist ~ fpco2 + ftemp + reef + fpco2:ftemp, data = dip_dist)
summary(p_dip_aov)
dip_dip_tuk <- TukeyHSD(p_dip_aov)

dip_dip_tab <- as.data.frame(dip_dip_tuk$`treat2:reef`)
dip_dip_tab$treat <- rownames(dip_dip_tab)

```

Reef environment:
```{r}

dip_dip_tuk$reef

```

Temperature:
```{r}

dip_dip_tuk$ftemp
```

*p*CO~2~:
```{r}

dip_dip_tuk$fpco2

```

<br/>
  
```{r plots of PSTR distances, fig.height = 3, fig.width = 10}

# just treatment
dip_dist_sum2 <- summarySE(measurevar = "dist", groupvars = c("fpco2", "ftemp", "reef"), data = dip_dist)
dip_dist_sum2$treat <- paste(dip_dist_sum2$fpco2, dip_dist_sum2$ftemp, sep = "_")
dip_dist$treat_plot <- ordered(dip_dist$treat_plot, levels = c("300_28", "300_31", "420_28", "420_31", "680_28", "680_31", "3300_28", "3300_31"))

dip_con_dis_plot <- ggplot(dip_dist_sum2) +
  theme_bw() +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="right", panel.border = element_rect(colour = "black", size= 0.8)) +
  #scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  ylab("Mean distance from control") +
  xlab("") +
  ylim(0, 7) +
  #geom_point(aes(x = treat, y = dist, colour = reef), position = dodge, alpha = 0.3, shape = 17, size = 2) +
  geom_point(aes(x = treat_plot, y = dist, colour = reef), position = dodge, alpha = 0.3, size = 2.5, data = dip_dist) +
  geom_errorbar(position = dodge, aes(x = treat, ymin = dist - se, ymax = dist + se, colour = reef), width = 0, size = 1.5) +
  geom_vline(xintercept = c(2.5, 4.5, 6.5)) +
  annotate("text", x = 1, y = 7, label = "pre-industrial") +
  annotate("text", x = 3, y = 7, label = "present-day") +
  annotate("text", x = 5.1, y = 7, label = "end-of-century") +
  annotate("text", x = 6.9, y = 7, label = "extreme") +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b"))
dip_con_dis_plot

```

---

<br/>


#### *P. astreoides*

aov(distance ~ *p*CO2 + temperature + reef)

```{r PAST distance dataframe setup}

a_dis <- a_pca$x[,1:2] # grab PC1 and PC2 distances from prcomp() object

por_dist <- cbind(a_df[,c(1,7,10,11,12,9,25)], a_dis) # combine the datasets

por_dist$cont_pc1[por_dist$treat2 == "447_28"] <- por_dist$PC1[por_dist$treat2 == "447_28"] # this adds column with the control value PC1 per colony
por_dist$cont_pc2[por_dist$treat2 == "447_28"] <- por_dist$PC2[por_dist$treat2 == "447_28"] # this adds column with the control value PC2 per colony

# get the 400_28 PC values
por_dist2 <- por_dist %>%  
  group_by(colony) %>% 
  summarise(con2_pc1 = sum(cont_pc1, na.rm = TRUE))
por_dist3 <- por_dist %>% 
  group_by(colony) %>% 
  summarise(con2_pc2 = sum(cont_pc2, na.rm = TRUE))

# Make columns of the 400_28 PC values
por_dist <- por_dist %>% 
  left_join(por_dist2, by = c("colony" = "colony"))
por_dist <- por_dist %>% 
  left_join(por_dist3, by = c("colony" = "colony"))

por_dist$dist <- sqrt(((por_dist$PC1 - por_dist$con2_pc1)^2) + ((por_dist$PC2 - por_dist$con2_pc2)^2)) # formula for calculating distance between control (T90) and treatment values
por_dist$treat_plot <- paste(por_dist$fpco2, por_dist$ftemp, sep = "_")

```

```{r PAST distance analysis}

a_por_aov <- aov(dist ~ fpco2 + ftemp + reef, data = por_dist)
summary(a_por_aov)
por_por_tuk <- TukeyHSD(a_por_aov)

por_por_tab <- as.data.frame(por_por_tuk$`treat2:reef`)
por_por_tab$treat <- rownames(por_por_tab)

```

Reef environment:
```{r}

por_por_tuk$reef

```

Temperature:
```{r}

por_por_tuk$ftemp

```

*p*CO~2~:
```{r}

por_por_tuk$fpco2

```

<br/>
  
```{r plots of PAST distances, fig.height = 3, fig.width = 10}

# just treatment
por_dist_sum2 <- summarySE(measurevar = "dist", groupvars = c("fpco2", "ftemp", "reef"), data = por_dist)
por_dist_sum2$treat <- paste(por_dist_sum2$fpco2, por_dist_sum2$ftemp, sep = "_")
por_dist$treat_plot <- ordered(por_dist$treat_plot, levels = c("300_28", "300_31", "420_28", "420_31", "680_28", "680_31", "3300_28", "3300_31"))

por_con_dis_plot <- ggplot(por_dist_sum2) +
  theme_bw() +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="right", panel.border = element_rect(colour = "black", size= 0.8)) +
  #scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  ylab("Mean distance from control") +
  xlab("") +
  ylim(0, 7) +
  #geom_point(aes(x = treat, y = dist, colour = reef), position = dodge, alpha = 0.3, shape = 17, size = 2) +
  geom_point(aes(x = treat_plot, y = dist, colour = reef), position = dodge, alpha = 0.3, size = 2.5, data = por_dist) +
  geom_errorbar(position = dodge, aes(x = treat, ymin = dist - se, ymax = dist + se, colour = reef), width = 0, size = 1.5) +
  geom_vline(xintercept = c(2.5, 4.5, 6.5)) +
  annotate("text", x = 1, y = 7, label = "pre-industrial") +
  annotate("text", x = 3, y = 7, label = "present-day") +
  annotate("text", x = 5.1, y = 7, label = "end-of-century") +
  annotate("text", x = 6.9, y = 7, label = "extreme") +
  scale_colour_manual("reef environment", labels = c("offshore", "inshore"), values = c("#00a08b", "#e9aa2b"))
por_con_dis_plot

```

---

<br/>



```{r full distance plot, fig.width = 10, fig.height = 9, eval = FALSE}

plot_grid(sid_con_dis_plot, dip_con_dis_plot, por_con_dis_plot, ncol = 1, labels = "AUTO")

#ggsave("Figure3_PCAdistance_24Jan20.pdf")

```

<br/>

### T0 Comparison 

#### *S. siderea*

**Questions to ask:**
* What should I use as a loading in my PCA?
* Calculating distance from T0/control mean or from colony value?

```{r testing PCA with T0}

df_plast <- subset(df, species != "T") 
df_plast <- df_plast[,-c(17:37)]
df_plast <- completeFun(df_plast, "den")
df_plast <- completeFun(df_plast, "host")
df_plast <- completeFun(df_plast, "lipid")
df_plast <- completeFun(df_plast, "carb")
df_plast$time <- gsub("T", "", df_plast$T0_T90)
df_plast$time <- as.numeric(df_plast$time)

## specific species dataframes
s_plast <- subset(df_plast, species == "S") 

# set up the dataframe
s_plast_l <- gather(s_plast, param, value, c(14:18))
s_plast$fpco2 <- factor(s_plast$fpco2, levels = c("300", "420", "680", "3300"))

s_pca_plast_mod <- adonis(value ~ treat2, data = s_plast_l, method='eu')
s_pca_plast_mod # view SSID adonis output

s_plast_pca <- prcomp(s_plast[,c(14:18)], center = TRUE, scale= TRUE)


s_plast$time2 <- factor(s_plast$time)

autoplot(s_plast_pca, data = s_plast, 
         colour = "time2",
         frame = TRUE, 
         frame.type = "norm",
         loadings = TRUE, 
         loadings.colour = "black", 
         loadings.label = TRUE,
         loadings.label.colour = "black",         
         loadings.label.size = 4, 
         loadings.label.hjust = -1, 
         loadings.label.vjust = 0.1,
         loadings.label.repel = TRUE) +
  scale_colour_manual("Time", labels = c("T0", "T90"),  values = c("#E69F00", "#56B4E9")) +
  scale_fill_manual("Time", labels = c("T0", "T90"), values = c(NA, NA)) +  
  #lims(x = c(-0.5,0.4), y = c(-0.4,0.4)) +
  guides(col = guide_legend(nrow = 2, byrow = TRUE, title.position = "top")) +  
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank(),strip.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA, size=1), legend.position = "bottom")
  #annotate("text", x = -0.39, y = -0.38, label = deparse(s_reef_pval), parse = TRUE, size = 3)

```


```{r SSID T0 distance dataframe setup}

s_plast_dis <- s_plast_pca$x[,1:2] # grab PC1 and PC2 distances from prcomp() object

sid_plast_dist <- cbind(s_plast, s_plast_dis) # combine the datasets

sid_plast_dist$cont_pc1[sid_plast_dist$treat2 == "T0"] <- sid_plast_dist$PC1[sid_plast_dist$treat2 == "T0"] # this adds column with the control value PC1 per colony
sid_plast_dist$cont_pc2[sid_plast_dist$treat2 == "T0"] <- sid_plast_dist$PC2[sid_plast_dist$treat2 == "T0"] # this adds column with the control value PC2 per colony

# get the 400_28 PC values
sid_plast_dist2 <- sid_plast_dist %>%  
  group_by(colony) %>% 
  summarise(con2_pc1 = sum(cont_pc1, na.rm = TRUE))
sid_plast_dist3 <- sid_plast_dist %>% 
  group_by(colony) %>% 
  summarise(con2_pc2 = sum(cont_pc2, na.rm = TRUE))

# Make columns of the 400_28 PC values
sid_plast_dist <- sid_plast_dist %>% 
  left_join(sid_plast_dist2, by = c("colony" = "colony"))
sid_plast_dist <- sid_plast_dist %>% 
  left_join(sid_plast_dist3, by = c("colony" = "colony"))

sid_plast_dist$dist <- sqrt(((sid_plast_dist$PC1 - sid_plast_dist$con2_pc1)^2) + ((sid_plast_dist$PC2 - sid_plast_dist$con2_pc2)^2)) # formula for calculating distance between control (T90) and treatment values
sid_plast_dist$treat_plot <- paste(sid_plast_dist$fpco2, sid_plast_dist$ftemp, sep = "_")


sid_plast_dist_sum2 <- summarySE(measurevar = "dist", groupvars = c("treat2", "reef"), data = sid_plast_dist)
#sid_plast_dist_sum2$treat <- paste(sid_plast_dist_sum2$fpco2, sid_plast_dist_sum2$ftemp, sep = "_")
#sid_plast_dist$treat_plot <- ordered(sid_plast_dist$treat_plot, levels = c("T", "300_28", "300_31", "420_28", "420_31", "680_28", "680_31", "3300_28", "3300_31"))

ggplot(sid_plast_dist_sum2) +
  theme_bw() +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), strip.text.x = element_blank(), panel.background=element_blank(), axis.line=element_line(color="black"), legend.key=element_blank(), strip.background = element_blank(), legend.position="right", panel.border = element_rect(colour = "black", size= 0.8)) +
  #scale_x_continuous(breaks = c(2, 4 ,6 ,8, 10), labels = c("T0", "300", "420", "680", "3300"))+
  ylab("Mean distance from control") +
  xlab("") +
  ylim(0, 7) +
  #geom_point(aes(x = treat, y = dist, colour = reef), position = dodge, alpha = 0.3, shape = 17, size = 2) +
  geom_point(aes(x = treat2, y = dist, colour = reef), position = dodge, alpha = 0.3, size = 2.5, data = sid_plast_dist) +
  geom_errorbar(position = dodge, aes(x = treat2, ymin = dist - se, ymax = dist + se, colour = reef), width = 0, size = 1.5)

aov(dist ~ treat2 + reef, data = sid_plast_dist)

summary(aov(dist ~ treat2 + reef, data = sid_plast_dist))

```





#### *P. strigosa*

#### *P. astreoides*

<br/>







```{r protein table, include=FALSE, eval = FALSE}

pro.tab <- df_pro_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
pro.tab$binder <- paste(pro.tab$species, pro.tab$treat2, sep = "_")

T90.pro.mean <- summarySE(data=pro.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.pro.low <- summarySE(data=pro.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.pro.up <- summarySE(data=pro.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

pro.tab <- cbind(T90.pro.mean, T90.pro.low, T90.pro.up)[, c(1,2,4,5,13,21)]
pro.tab$mean <- round(pro.tab$mean, 2)
pro.tab$lowerci <- round(pro.tab$lowerci, 2)
pro.tab$upperci <- round(pro.tab$upperci, 2)

colnames(pro.tab)[colnames(pro.tab)=="treat2"] <- "treatment"
colnames(pro.tab)[colnames(pro.tab)=="lowerci"] <- "lower 95%"
colnames(pro.tab)[colnames(pro.tab)=="upperci"] <- "upper 95%"
pro.tab$treatment <- factor(pro.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table1 <- kable(pro.tab[,-c(1)], booktabs = T, caption = "Table 1. T90 modeled mean coral host protein content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table1

```

```{r lipid table, include=FALSE, eval = FALSE}

lipid.tab <- df_lipid_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
lipid.tab$binder <- paste(lipid.tab$species, lipid.tab$treat2, sep = "_")

T90.lipid.mean <- summarySE(data=lipid.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.lipid.low <- summarySE(data=lipid.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.lipid.up <- summarySE(data=lipid.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

lipid.tab <- cbind(T90.lipid.mean, T90.lipid.low, T90.lipid.up)[, c(1,2,4,5,13,21)]
lipid.tab$mean <- round(lipid.tab$mean, 2)
lipid.tab$lowerci <- round(lipid.tab$lowerci, 2)
lipid.tab$upperci <- round(lipid.tab$upperci, 2)

colnames(lipid.tab)[colnames(lipid.tab)=="treat2"] <- "treatment"
colnames(lipid.tab)[colnames(lipid.tab)=="lowerci"] <- "lower 95%"
colnames(lipid.tab)[colnames(lipid.tab)=="upperci"] <- "upper 95%"
lipid.tab$treatment <- factor(lipid.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table2 <- kable(lipid.tab[,-c(1)], booktabs = T, caption = "Table 2. T90 modeled mean coral host lipid content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table2

```

```{r carbohydrate table, include=FALSE, eval = FALSE}

carb.tab <- df_carb_a[,c(9,15,18:20)] #subset for species, treatment, and model values
carb.tab$binder <- paste(carb.tab$species, carb.tab$treat2, sep = "_")

T90.carb.mean <- summarySE(data=carb.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.carb.low <- summarySE(data=carb.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.carb.up <- summarySE(data=carb.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

carb.tab <- cbind(T90.carb.mean, T90.carb.low, T90.carb.up)[, c(1,2,4,5,13,21)]
carb.tab$mean <- round(carb.tab$mean, 2)
carb.tab$lowerci <- round(carb.tab$lowerci, 2)
carb.tab$upperci <- round(carb.tab$upperci, 2)

colnames(carb.tab)[colnames(carb.tab)=="treat2"] <- "treatment"
colnames(carb.tab)[colnames(carb.tab)=="lowerci"] <- "lower 95%"
colnames(carb.tab)[colnames(carb.tab)=="upperci"] <- "upper 95%"
carb.tab$treatment <- factor(carb.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table3 <- kable(carb.tab[,-c(1)], booktabs = T, caption = "Table 3. T90 modeled mean coral host carbohydrate content and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table3

```

```{r density table, include=FALSE, eval = FALSE}

den.tab <- df_den_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
den.tab$binder <- paste(den.tab$species, den.tab$treat2, sep = "_")

T90.den.mean <- summarySE(data=den.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.den.low <- summarySE(data=den.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.den.up <- summarySE(data=den.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

den.tab <- cbind(T90.den.mean, T90.den.low, T90.den.up)[, c(1,2,4,5,13,21)]
den.tab$mean <- round(den.tab$mean, 2)
den.tab$lowerci <- round(den.tab$lowerci, 2)
den.tab$upperci <- round(den.tab$upperci, 2)

colnames(den.tab)[colnames(den.tab)=="treat2"] <- "treatment"
colnames(den.tab)[colnames(den.tab)=="lowerci"] <- "lower 95%"
colnames(den.tab)[colnames(den.tab)=="upperci"] <- "upper 95%"
den.tab$treatment <- factor(den.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table4 <- kable(den.tab[,-c(1)], booktabs = T, caption = "Table 4. T90 modeled mean algal endosymbiont cell density and 95% confidence intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table4

```

```{r chlorophyll table, include=FALSE, eval = FALSE}

chla.tab <- df_chla_a[,c(9,15,18:20)] #subset for species, treatment, parameter, and model values
chla.tab$binder <- paste(chla.tab$species, chla.tab$treat2, sep = "_")

T90.chla.mean <- summarySE(data=chla.tab, measurevar = "mean", groupvars = c("species", "treat2", "binder"))
T90.chla.low <- summarySE(data=chla.tab, measurevar = "lowerci", groupvars = c("species", "treat2", "binder"))
T90.chla.up <- summarySE(data=chla.tab, measurevar = "upperci", groupvars = c("species", "treat2", "binder"))

chla.tab <- cbind(T90.chla.mean, T90.chla.low, T90.chla.up)[, c(1,2,4,5,13,21)]
chla.tab$mean <- round(chla.tab$mean, 2)
chla.tab$lowerci <- round(chla.tab$lowerci, 2)
chla.tab$upperci <- round(chla.tab$upperci, 2)

colnames(chla.tab)[colnames(chla.tab)=="treat2"] <- "treatment"
colnames(chla.tab)[colnames(chla.tab)=="lowerci"] <- "lower 95%"
colnames(chla.tab)[colnames(chla.tab)=="upperci"] <- "upper 95%"
chla.tab$treatment <- factor(chla.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table5 <- kable(chla.tab[,-c(1)], booktabs = T, caption = "Table 5. T90 modeled mean algal endosymbiont chlorophyll a content and 95% confichlace intervals for each  species") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table5

```

```{r host table, include=FALSE, eval = FALSE}

host.tab <- df_host_a[,c(9,15,16,18:20)] #subset for species, treatment, parameter, and model values
host.tab$binder <- paste(host.tab$species, host.tab$param, host.tab$treat2, sep = "_")

T90.host.mean <- summarySE(data=host.tab, measurevar = "mean", groupvars = c("species", "param", "treat2", "binder"))
T90.host.low <- summarySE(data=host.tab, measurevar = "lowerci", groupvars = c("species", "param", "treat2", "binder"))
T90.host.up <- summarySE(data=host.tab, measurevar = "upperci", groupvars = c("species", "param", "treat2", "binder"))

host.tab <- cbind(T90.host.mean, T90.host.low, T90.host.up)[, c(1,3,5,6,15,24)]
host.tab$mean <- round(host.tab$mean, 2)
host.tab$lowerci <- round(host.tab$lowerci, 2)
host.tab$upperci <- round(host.tab$upperci, 2)

colnames(host.tab)[colnames(host.tab)=="treat2"] <- "treatment"
colnames(host.tab)[colnames(host.tab)=="lowerci"] <- "lower 95%"
colnames(host.tab)[colnames(host.tab)=="upperci"] <- "upper 95%"
host.tab$treatment <- factor(host.tab$treatment, c("T0", "288_28", "311_31", "447_28", "405_31", "673_28", "701_31", "3285_28", "3309_31"))

table6 <- kable(host.tab[,-c(1)], booktabs = T, caption = "Table 6. Total coral host physiology at T90 modeled mean and 95% confidence intervals for each physiological parameter per species ") %>%
  kable_styling(font_size = 10, full_width = F) %>% 
  pack_rows("(a) SSID", 1, 9) %>%
  pack_rows("(b) PSTR", 10, 18) %>%
  pack_rows("(c) PAST", 19, 27)
table6

```


```{r excel WB, include=FALSE, eval = FALSE}

### Create workbook
wb <- createWorkbook()

# add 'Table 1' worksheet
addWorksheet(wb, "Table 1 - protein") 
writeData(wb, sheet = 1, x = pro.tab)
setColWidths(wb, sheet = 1, cols = 1:5, widths = "auto")

# add 'Table 2' worksheet
addWorksheet(wb, "Table 2 - lipid") 
writeData(wb, sheet = 2, x = lipid.tab)
setColWidths(wb, sheet = 2, cols = 1:5, widths = "auto")

# add 'Table 3' worksheet
addWorksheet(wb, "Table 3 - carbohydrate") 
writeData(wb, sheet = 3, x = carb.tab)
setColWidths(wb, sheet = 3, cols = 1:5, widths = "auto")

# add 'Table 4' worksheet
addWorksheet(wb, "Table 4 - density") 
writeData(wb, sheet = 4, x = den.tab)
setColWidths(wb, sheet = 4, cols = 1:5, widths = "auto")

# add 'Table 5' worksheet
addWorksheet(wb, "Table 5 - chlorophyll") 
writeData(wb, sheet = 5, x = chla.tab)
setColWidths(wb, sheet = 5, cols = 1:5, widths = "auto")

# add 'Table 6' worksheet
addWorksheet(wb, "Table 6 - total host") 
writeData(wb, sheet = 6, x = host.tab)
setColWidths(wb, sheet = 6, cols = 1:5, widths = "auto")

# add 'Table 7' worksheet
addWorksheet(wb, "Table 7 - SSID dist") 
writeData(wb, sheet = 7, x = sid.dis.tab)
setColWidths(wb, sheet = 7, cols = 1:5, widths = "auto")

# add 'Table 8' worksheet
addWorksheet(wb, "Table 8 - PAST dist") 
writeData(wb, sheet = 8, x = por.dis.tab)
setColWidths(wb, sheet = 8, cols = 1:5, widths = "auto")


# save workbook
saveWorkbook(wb, file="Ch3_Phys_tables.xlsx", overwrite = TRUE)


```



<br/>
<br/>
<br/>

## Session information

Session information from the last run date on `r date`:

```{r}
sessionInfo()
```


